### 2024-03-11 outputs/paper/Freewill_in_gig_work.qmd
Initial commit

---
title: "The Freedom of Choice in the Gig Economy "
subtitle: "Belief in Free Will Positively Predicts Job Satisfaction"
author: 
  - Mingjia Chen
  - Hadi Ahmad
  - Tianen (Evan) Hao
thanks: "Code and data are available at: https://github.com/ShadyEvan4830/Freewill_Analysis/tree/main; Replication on Social Science Reproduction: https://doi.org/10.48152/ssrp-m0r5-q824 (Please click the [URL](https://www.socialsciencereproduction.org/reproductions/26b6954c-44ec-4eba-afbb-e19847958dc8/index) instead since DOI is unavaliable currently as it is being reviewed/loaded by the platform)"
platform available at: TBA"
date: February 11, 2024
date-format: long
abstract: "In the area of work and personal beliefs, the concept of free will has a key impact on job satisfaction, with people from different demographic backgrounds having various views based on their unique circumstances. We conducted a replication study of the paper by Feldman et al. (2018) regarding the gig economy within Amazon Mechanical Turk and found a strong positive correlation between individuals’ beliefs about free will and their job satisfaction, significantly mediated by perceived autonomy. Since the gig economy is such an essential part of society today, replicating this study will advance the conversation about how beliefs about free will impact job satisfaction in non-traditional work settings."
format: pdf
toc: true
number-sections: true
bibliography: bibliography.bib
---

```{r}
#| include: false
#| warning: false
#| message: false
#download the packages if necessary, then load the packages
if (!require("pacman")) install.packages("pacman")
pacman::p_load(haven, psych,dplyr,tidyverse, knitr, kableExtra, ltm)

# Load the package
library(psych)
library(dplyr)
library(tidyverse)
library(knitr)
library(kableExtra)

# Read the data
data <- read_csv("outputs/data/FW_satisfaction-Study_2-data.csv")
```

```{r}
#| include: false
#| warning: false
#| message: false

## Helper Function
## Author: Paul van der Laken (2020)
## Link: https://www.r-bloggers.com/2020/07/create-a-publication-ready-correlation-matrix-with-significance-levels-in-r/

#' correlation_matrix
#' Creates a publication-ready / formatted correlation matrix, using `Hmisc::rcorr` in the backend.
#'
#' @param df dataframe; containing numeric and/or logical columns to calculate correlations for
#' @param type character; specifies the type of correlations to compute; gets passed to `Hmisc::rcorr`; options are `"pearson"` or `"spearman"`; defaults to `"pearson"`
#' @param digits integer/double; number of decimals to show in the correlation matrix; gets passed to `formatC`; defaults to `3`
#' @param decimal.mark character; which decimal.mark to use; gets passed to `formatC`; defaults to `.`
#' @param use character; which part of the correlation matrix to display; options are `"all"`, `"upper"`, `"lower"`; defaults to `"all"`
#' @param show_significance boolean; whether to add `*` to represent the significance levels for the correlations; defaults to `TRUE`
#' @param replace_diagonal boolean; whether to replace the correlations on the diagonal; defaults to `FALSE`
#' @param replacement character; what to replace the diagonal and/or upper/lower triangles with; defaults to `""` (empty string)
#'
#' @return a correlation matrix
#' @export
#'
#' @examples
#' `correlation_matrix(iris)`
#' `correlation_matrix(mtcars)`
correlation_matrix <- function(df, 
                               type = "pearson",
                               digits = 3, 
                               decimal.mark = ".",
                               use = "all", 
                               show_significance = TRUE, 
                               replace_diagonal = FALSE, 
                               replacement = ""){

  # check arguments
  stopifnot({
    is.numeric(digits)
    digits >= 0
    use %in% c("all", "upper", "lower")
    is.logical(replace_diagonal)
    is.logical(show_significance)
    is.character(replacement)
  })
  # we need the Hmisc package for this
  require(Hmisc)

  # retain only numeric and boolean columns
  isNumericOrBoolean = vapply(df, function(x) is.numeric(x) | is.logical(x), logical(1))
  if (sum(!isNumericOrBoolean) > 0) {
    cat('Dropping non-numeric/-boolean column(s):', paste(names(isNumericOrBoolean)[!isNumericOrBoolean], collapse = ', '), '\n\n')
  }
  df = df[isNumericOrBoolean]

  # transform input data frame to matrix
  x <- as.matrix(df)

  # run correlation analysis using Hmisc package
  correlation_matrix <- Hmisc::rcorr(x, type = )
  R <- correlation_matrix$r # Matrix of correlation coeficients
  p <- correlation_matrix$P # Matrix of p-value

  # transform correlations to specific character format
  Rformatted = formatC(R, format = 'f', digits = digits, decimal.mark = decimal.mark)

  # if there are any negative numbers, we want to put a space before the positives to align all
  if (sum(R < 0) > 0) {
    Rformatted = ifelse(R > 0, paste0(' ', Rformatted), Rformatted)
  }

  # add significance levels if desired
  if (show_significance) {
    # define notions for significance levels; spacing is important.
    stars <- ifelse(is.na(p), "   ", ifelse(p < .001, "***", ifelse(p < .01, "** ", ifelse(p < .05, "*  ", ifelse(p < .10, "+  " ,"   ")))))
    Rformatted = paste0(Rformatted, stars)
  }
  # build a new matrix that includes the formatted correlations and their significance stars
  Rnew <- matrix(Rformatted, ncol = ncol(x))
  rownames(Rnew) <- colnames(x)
  colnames(Rnew) <- paste(colnames(x), "", sep =" ")

  # replace undesired values
  if (use == 'upper') {
    Rnew[lower.tri(Rnew, diag = replace_diagonal)] <- replacement
  } else if (use == 'lower') {
    Rnew[upper.tri(Rnew, diag = replace_diagonal)] <- replacement
  } else if (replace_diagonal) {
    diag(Rnew) <- replacement
  }

  return(Rnew)
}

```

# Introduction

The intersection of agency beliefs and workplace outcomes has become a focal point of contemporary psychological research, revealing nuanced insights into how deeply held convictions shape our professional experiences. @feldman seminal investigation into the dynamics of free will beliefs and job satisfaction unveils a pivotal link, positing that individuals' conviction in their autonomy significantly forecasts their contentment at work. Their research amplifies our understanding of the psychological underpinnings of job satisfaction and propels a discourse on the broader societal and cultural factors that sculpt our professional well-being. This paper seeks to build upon Feldman and other scholars' [@feldman] foundational research, extending its theoretical and empirical contributions to examine the implications of free will beliefs in a distinct yet paralleled context. Our focus shifts towards the burgeoning realm of digital workplaces, explicitly examining the phenomenon within Amazon's Mechanical Turk (MTurk) community. Amazon Mechanical Turk (MTurk) is a crowdsourcing marketplace operated by Amazon where individuals and businesses can outsource tasks and processes to a distributed workforce who can perform these tasks virtually. Our study is poised to explore whether the nuanced dynamics of agency beliefs within the digital gig economy can shed light on the positive ramifications of free will beliefs on job satisfaction among a global workforce engaged in micro-tasks.

The gig economy's rise reshapes work, offering greater autonomy but uncertain income and benefits. This shift necessitates a new understanding of free will's role in modern job satisfaction as workers navigate the trade-offs between flexibility and stability. Through this lens, we aim to contribute a fresh perspective to the discourse on free will and job satisfaction, underpinned by robust empirical evidence and a comprehensive analysis of its implications in contemporary work environments.

This paper uses the statistical programming language R [@citeR] and related libraries such as `tidyverse` [@tidyverse], `janitor` [@janitor], `ggplot2` [@ggplot2], `dplyr` [@dplyr], `readr ` [@readr], `tibble` [@tibble], `kableExtra` [@kableExtra], `psych` [@psych], `haven`[@haven], `Hmisc` [@Hmisc], and `knitr` [@knitr] to analyze the gig economy and Amazon Mechanical Turk. It is structured by summarizing the study's purpose, methods, and results and emphasizing the positive correlation between free will beliefs and job satisfaction. The introduction introduces the background and outlines the structure of the paper. The data and results sections present each study's design, questions, and variables with figures and tables @fig-descrip, @fig-beliefs-vs-satis, @tbl-corr-between-subscales, @tbl-demo-corr, and @tbl-Means-SD-Corr. We aim to highlight the use of Likert-type scales and the focus on autonomy, job satisfaction, and free will beliefs. The replication process and the tools used for data analysis are also mentioned, providing a foundation for understanding how the study was conducted and analyzed. The discussion explains these findings and points out their theoretical and practical implications; in addition, in order to further confirm the validity of the original paper and our analysis, we selected another peer-reviewed professional academic journal @Baldissarri as a reference for comparison and to support our opinions. Ethical considerations and biases in accounting address research integrity issues. The conclusion reiterates the study's contribution to understanding job satisfaction in nontraditional work settings. References provide supplementary information and scholarly resources.

# Data

## Data Tools

The original paper was based on three studies conducted by the authors, with data that can be found on the `Open Science Foundation (OSF)` website. The provided data [@feldman] was replicated in `R` [@citeR], with the goal of determining if there are any errors in the models, and what more can be learned and applied in a Canadian context. The libraries mentioned above are used for supplementary analysis. The goal of the original study was to understand if a relationship exists between a belief of free will and job satisfaction in different cultural contexts.

## Methodology

The original paper was based on two studies conducted by the authors, and secondary data comprising the third study. The questions were translated from English to Chinese and back to English by senior researchers fluent in both languages, due to language differences in Study 2. These translations were cross-verified by another senior researcher also fluent in both languages, to ensure the responses accurately captured the sentiments of the respondents.

### Study 1

In the first study, eight questions were asked about free will and three questions about job satisfaction using a Likert-type scale. It looked at responses from 252 real estate agents in Taiwan. The goal of the study was to determine if there was a correlation between the belief of free will and job satisfaction for the chosen respondents, and to test if a three-month delay introduced any variation in results. Each variable represents a question that respondents answered, containing the value provided by the respondent from the survey. This value is stored as an integer ranging from 1 (strongly disagree) to 5 or 6 depending on the question (strongly agree) (Appendix @sec-study1). As a result, the data is available not just as an aggregate, but for each anonymized respondent. Additional variables are included to store the age and gender of respondents.

### Study 2

The second study focused on 137 American freelance workers, with a different set of survey questions examining a broader range of metrics on free will and satisfaction using a Likert-type scale (@fig-descrip). The goal of the second study was to test if the results of the first study could be applied to other contexts, to test if other agency factors affected the results, and to assess if a six-month delay introduced any variation in results. These questions can be broken down into the categories of job satisfaction, job autonomy, self-efficiency, free will, self-control, locus of control, self-esteem, self-efficacy, and implicit beliefs (Appendix @sec-study2). Data on these additional variables was collected to examine if controlling for differences in factors like locus of control led to any differences in job satisfaction. Each variable represents a question that respondents answered, containing the value provided by the respondent from the survey. This value is stored as an integer ranging from 1 (strongly disagree) to 5 or 6 depending on the question (strongly agree). The answers to the locus of control questions serve as an exception, storing a sum of values by assigning a 0 or 1 depending on which option was chosen for a set of 13 questions. As a result, the data is available not just as an aggregate, but for each anonymized respondent. Additional variables are included to store the age and gender of respondents.

```{r}
#| label: fig-descrip
#| fig-cap: Descriptive summary of Job Satisfaction Likert Scale Results
#| fig-subcap: ["Job Satisfaction (T1)","Job Satisfaction (T2)","Beilef in Free Will"]
#| layout-ncol: 2
#| echo: false
#| warning: false
#| message: false

data_freq <- read.csv("outputs/data/jobsatT1_data_freq.csv")           
# Create the bar chart
ggplot(data_freq, aes(x = Question, y = Percent, fill = factor(Response))) +
  geom_bar(stat = "identity") +
  scale_fill_brewer(palette = "Blues", name = "Response") +
  labs(x = "Question", y = "Percentage",caption = "Note. 1 = strongly disagree, 7 = strongly agree") +
  theme_minimal() +
  theme(legend.position = "bottom")

data2_freq <- read.csv("outputs/data/jobsatT2_data_freq.csv") 
# Create the bar chart
ggplot(data2_freq, aes(x = Question, y = Percent, fill = factor(Response))) +
  geom_bar(stat = "identity") +
  scale_fill_brewer(palette = "Blues", name = "Response") +
  labs(x = "Question", y = "Percentage",caption = "Note. 1 = strongly disagree, 7 = strongly agree") +
  theme_minimal() +
  theme(legend.position = "bottom")

data_freq3 <- read.csv("outputs/data/FW_data_freq.csv")           
# Create the bar chart
ggplot(data_freq3, aes(x = Question, y = Percent, fill = factor(Response))) +
  geom_bar(stat = "identity") +
  scale_fill_brewer(palette = "Blues", name = "Response") +
  labs(x = "Question", y = "Percentage",caption = "Note. 1 = strongly disagree, 7 = strongly agree") +
  theme_minimal() +
  theme(legend.position = "bottom")
```

\break

### Study 3

The third study relied on secondary data in the form of the World Values Survey, featuring over 14,000 respondents from 16 countries. The original dataset was not made available, and thus could not be replicated in this paper. Three variables were chosen from this dataset (Appendix @sec-study3).

## Replication

The original authors used `SPSS` to run analyses on their findings. Data from studies 1 and 2 was provided in the replication package on `OSF` as SPS and SAV files, along with a version compiled into a spreadsheet. For this paper, we used `R` to replicate the findings by using `haven` to read in the data. This caused some incongruencies in the results, with a lower p-value on some variables.

# Results

## Main Findings

Our analysis revealed a consistent positive correlation between beliefs in free will and job satisfaction across different cultural contexts. For instance, in @fig-beliefs-vs-satis, we observed a clear upward trend among Taiwanese real estate agents, where stronger free will beliefs were associated with higher job satisfaction; this analysis results from Study 1 can be used as a non-same type of worker situation to potentially support the relationship between free will and job satisfaction of Amazon American gig workers. Later, we found similar results for Amazon American gig workers; @fig-beliefs-vs-satis illustrates the same pattern among American gig workers. These trends suggest that the perception of autonomy can significantly enhance job contentment.

## Reliability of Subscales

We conducted an analysis in terms of the reliability of the subscales used for determining participants’ responses regarding different variables (@tbl-corr-between-subscales). In @tbl-corr-between-subscales, the internal consistency (Cronbach’s alpha) of each subscale and the correlations between each combination are calculated to speculate the reliability and validity of the data set we used for the study. According to the results in @tbl-corr-between-subscales, although not strong, the subscales correlate significantly (p < .01) with the variables we would like to capture and study for the analysis. This means that these subscales and the data set are reliable to use for this paper.

\newpage
```{r}
#| label: tbl-corr-between-subscales
#| tbl-cap: Correlations between free will subscales and job satisfaction
#| echo: false
#| warning: false
#| message: false

## Table 2 (Appendix) - Correlations between free will subscales and job satisfaction

#Correlations between free will subscales and job satisfaction
# Select the variables for correlation analysis
selected_variables_2 <-data[, c("jobsatT1", "jobsatT2", "FWDfw", "FWDagency", "FWDmoral","FWDresp",
                              "FWDpower","FWDlimit","FWDall","FWDfwagency","FWself","FWgeneral")]

# Compute pairwise correlations
correlation_matrix_2 <-correlation_matrix(selected_variables_2[,1:12], digits = 2, use = 'lower', replace_diagonal = TRUE)

#choose desired rows and columns
correlation_matrix_2 <- correlation_matrix_2[c('FWDfwagency','FWDall','FWDfw','FWDagency','FWDmoral','FWDpower',
                                               "FWDresp",'FWDlimit','FWself','FWgeneral'),]
correlation_matrix_2 <- correlation_matrix_2[,c('jobsatT1 ','jobsatT2 ')]

#rename columns and rows 
colnames(correlation_matrix_2)[colnames(correlation_matrix_2) == "jobsatT1 "] <- "Job satisfaction T1"
colnames(correlation_matrix_2)[colnames(correlation_matrix_2) == "jobsatT2 "] <- "Job satisfaction T2"

rownames(correlation_matrix_2)[rownames(correlation_matrix_2) == "FWDfwagency"] <- "FW T1 Agency and free will subscales"
rownames(correlation_matrix_2)[rownames(correlation_matrix_2) == "FWDall"] <- "FW T1 All subscales combined"
##ATTENTION: may need to modift the all subscale
rownames(correlation_matrix_2)[rownames(correlation_matrix_2) == "FWDfw"] <- "FW T1 Free will subscale"
rownames(correlation_matrix_2)[rownames(correlation_matrix_2) == "FWDagency"] <- "FW T1 Personal agency subscale"
rownames(correlation_matrix_2)[rownames(correlation_matrix_2) == "FWDmoral"] <- "FW T1 Moral responsibility subscale"
rownames(correlation_matrix_2)[rownames(correlation_matrix_2) == "FWDpower"] <- "FW T1 Higher power control subscale (R)"
rownames(correlation_matrix_2)[rownames(correlation_matrix_2) == "FWDresp"] <- "FW T1 Personal responsibility subscale"
rownames(correlation_matrix_2)[rownames(correlation_matrix_2) == "FWDlimit"] <- "FW T1 Personal limitations subscale (R)"

rownames(correlation_matrix_2)[rownames(correlation_matrix_2) == "FWself"] <- "FW T1 - Personal"
rownames(correlation_matrix_2)[rownames(correlation_matrix_2) == "FWgeneral"] <- "FW T1 - General"

kable(correlation_matrix_2) |>
  kable_styling() |>
  row_spec(c(2,8), hline_after = TRUE)

```
*Note.* T1 = collected in Time 1, T2 = collected in Time 2   
\*p <.05. \*\*p<.01.\***p<.001.

## Demographic Factors

Demographic factors age and gender are speculated as well to see possible influence on job satisfaction with the combination of belief in free will. As the results in @tbl-demo-corr show, age and gender have a significant impact on belief in free will (p < .01); however, without these two demographic factors, belief in free will continues to significantly predict job satisfaction ((p < .001). This result ensures the significance of the relationship between one’s belief in free will and job satisfaction.

```{r}
#| label: tbl-demo-corr
#| tbl-cap: Controlling for demographics
#| echo: false
#| warning: false
#| message: false

## Table 3-Controlling for demographics

alphas1 <- c(0,0,0,0,0)
###### Cronbach’s Alpha coefficients
### Job statisfaction T1###
# Running reliability analysis
reliability_result <- psych::alpha(data[,c("jobsat_1","jobsat_2","jobsat_3r","jobsat_4","jobsat_5r")])
# Displaying reliability statistics
alphas1[1] <-(reliability_result$total$raw_alpha)

### Job satisfaction T2###
reliability_result <- psych::alpha(data[,c("jobsat2_1","jobsat2_2","jobsat2_3r","jobsat2_4","jobsat2_5r")])
alphas1[2] <-(reliability_result$total$raw_alpha)

### Beliefs in free will T1 ##
reliability_result <- psych::alpha(data[,c("fw_1", "fw_2", "fw_3", "fw_4", "fw_5", 
                                           "fw_6", "fw_7", "fw_8", "fw_9")])
alphas1[3] <-(reliability_result$total$raw_alpha)

### Job autonomy T1###
reliability_result <- psych::alpha(data[,c("jobaut_3", "jobaut_4","jobaut_5")])
alphas1[4] <-(reliability_result$total$raw_alpha)

### Job autonomy T2###
reliability_result <- psych::alpha(data[,c("jobaut2_3", "jobaut2_4","jobaut2_5")])
alphas1[5] <-(reliability_result$total$raw_alpha)

## round alphas into 2 digits
alphas1 <- round(alphas1,2)

selected_variables_3 <-data[, c("FWDfwagency","jobsatT1", "jobsatT2","age","gender")]

# Compute pairwise correlations
correlation_matrix_3 <- correlation_matrix(selected_variables_3[,1:5], digits = 2)
#choose desired rows and columns
correlation_matrix_3 <- correlation_matrix_3[,c('FWDfwagency ','jobsatT1 ','jobsatT2 ')]

#rename columns and rows 
colnames(correlation_matrix_3)[colnames(correlation_matrix_3) == "FWDfwagency "] <- "Belief in free will (T1)"
colnames(correlation_matrix_3)[colnames(correlation_matrix_3) == "jobsatT1 "] <- "Job satisfaction (T1)"
colnames(correlation_matrix_3)[colnames(correlation_matrix_3) == "jobsatT2 "] <- "Job satisfaction (T2)"

rownames(correlation_matrix_3)[rownames(correlation_matrix_3) == "FWDfwagency"] <- "Belief in free will (T1)"
rownames(correlation_matrix_3)[rownames(correlation_matrix_3) == "jobsatT1"] <- "Job satisfaction (T1)"
rownames(correlation_matrix_3)[rownames(correlation_matrix_3) == "jobsatT2"] <- "Job satisfaction (T2)"
rownames(correlation_matrix_3)[rownames(correlation_matrix_3) == "age"] <- "Age"
rownames(correlation_matrix_3)[rownames(correlation_matrix_3) == "gender"] <- "Gender"

correlation_matrix_3[1,1] <- paste("(" ,alphas1[3],")")
correlation_matrix_3[2,2] <- paste("(" ,alphas1[1],")")
correlation_matrix_3[3,3] <- paste("(" ,alphas1[2],")")
kable(correlation_matrix_3,booktabs = TRUE) |>
  kable_styling() |>
  row_spec(3, hline_after = TRUE)

```
*Note.* T1 = collected in Time 1, T2 = collected in Time 2; diagonal values are reliability alpha coefficients. Values under diagonal are two-tailed correlations whereas above are partial correlations controlling for age and gender (T1). Gender is coded as 0 = Male, 1 = Female. 
+p<.10. \*p <.05. \*\*p<.01.\***p<.001.

## Detailed Analysis and Trends

The original paper by @feldman demonstrates that a strong belief in free will results in significant increases in job satisfaction; this correlation is relevant across cultural differences and in different work fields (e.g., from Taiwanese real estate agents to American digital labour) similar results were maintained.

Through this paper, we conducted a replication study on institutional beliefs in the digital gig economy (specifically the MTurk community) and sought to determine whether there is a positive relationship between U.S. workers’ beliefs about free will and their job satisfaction with Amazon Mechanical. Based on an analysis of information from a six-month focused study of Amazon MTurk workers presented and other related auxiliary analyses of different industries in the original paper, our results confirm a positive relationship, indicating that workers with a stronger belief in free will tend to report higher levels of job satisfaction. Our analysis shows that the correlation between free will beliefs and job satisfaction is more vital in this digital microtask environment than in a traditional work environment. The above reinforces the idea that institutional beliefs in the increasingly prevalent gig economy are not just philosophical abstractions but have real consequences for workforce well-being.

```{r}
#| label: fig-beliefs-vs-satis
#| fig-cap: Beliefs in Free will vs. Job Satisfaction between Two Populations
#| fig-subcap: ["Taiwanese Real-estate Agents (Study 1)","US Online Labour Market Workers (Study 2)"]
#| layout-ncol: 2
#| echo: false
#| warning: false
#| message: false

data_TW <- read_csv("outputs/data/FW satisfaction-Study 1-data.csv")

lm_fit_TW <- lm(FW ~ JS, data=data_TW)

jobsat <- rowMeans(data[, c("jobsatT1", "jobsatT2")])

lm_fit <- lm(FWDfwagency ~ jobsat, data=data)

data_TW |>
  ggplot(aes(x = FW, y = JS)) +
  geom_point(color='blue') +
  geom_smooth(method='lm', se = FALSE, col = "black") +
  theme_minimal() +
  labs(x = "Free Will Belief", y = "Job satisfaction") +
  scale_color_brewer(palette = "Set1")

data |>
  ggplot(aes(x = FWDfwagency, y = jobsat)) +
  geom_point(color='red') +
  geom_smooth(method='lm', se = FALSE, col = "black") +
  theme_minimal() +
  labs(x = "Free Will Belief", y = "Job satisfaction") +
  scale_color_brewer(palette = "Set1")

```

Corresponding to @fig-beliefs-vs-satis, @tbl-Means-SD-Corr presents a quantitative synthesis of the relationship between free will beliefs and job satisfaction at two different time points. For example, the belief in free will at Time 1 (T1) had a correlation of 0.31** with job satisfaction at T1, and this association remained strong at Time 2 (T2). The statistical significance marked by ** (p<0.001) indicates a robust relationship that persisted over time.

\newpage
```{r}
#| label: tbl-Means-SD-Corr
#| tbl-cap: Study 2 Means, Standard Deviations, and Correlations
#| echo: false
#| warning: false
#| message: false

# Select the variables for correlation analysis
selected_variables <-data[, c("jobsatT1", "jobsatT2", "FWDfwagency", "jobautT1", "jobautT2", "locus", "ess_kind", "selfest", "selfeff", "selfcontrol")]

# Compute pairwise correlations
correlation_matrix_1 <- correlation_matrix(selected_variables[,1:10], digits = 2, use = 'lower', replace_diagonal = TRUE)

# modifying the format so it matches to the correlation table like in paper
## making the upper right part zero

## Add Mean and SD
M <- c(mean(selected_variables$jobsatT1), mean(selected_variables$jobsatT2,na.rm = TRUE), mean(selected_variables$FWDfwagency),
       mean(selected_variables$jobautT1,na.rm = TRUE),mean(selected_variables$jobautT2,na.rm = TRUE),mean(selected_variables$locus),
       mean(selected_variables$ess_kind),mean(selected_variables$selfest),mean(selected_variables$selfeff),
       mean(selected_variables$selfcontrol))

M <- round(M,2)

SD <- c(sd(selected_variables$jobsatT1), sd(selected_variables$jobsatT2,na.rm = TRUE), sd(selected_variables$FWDfwagency),
        sd(selected_variables$jobautT1,na.rm = TRUE),sd(selected_variables$jobautT2,na.rm = TRUE),sd(selected_variables$locus),
        sd(selected_variables$ess_kind),sd(selected_variables$selfest),sd(selected_variables$selfeff),
        sd(selected_variables$selfcontrol))

SD <- round(SD,2)

#choose desired rows
correlation_matrix_1 <- correlation_matrix_1[ ,c('jobsatT1 ','jobsatT2 ','FWDfwagency ','jobautT1 ','jobautT2 ')]

correlation_matrix_1<- cbind(M,SD, correlation_matrix_1)

#rename columns and rows in r
colnames(correlation_matrix_1)[colnames(correlation_matrix_1) == "jobsatT1 "] <- "(T1)"
colnames(correlation_matrix_1)[colnames(correlation_matrix_1) == "jobsatT2 "] <- "(T2)"
colnames(correlation_matrix_1)[colnames(correlation_matrix_1) == "FWDfwagency "] <- "(T1)"
colnames(correlation_matrix_1)[colnames(correlation_matrix_1) == "jobautT1 "] <- "(T1)"
colnames(correlation_matrix_1)[colnames(correlation_matrix_1) == "jobautT2 "] <- "(T2)"

rownames(correlation_matrix_1)[rownames(correlation_matrix_1) == "jobsatT1"] <- "Job satisfaction(T1)"
rownames(correlation_matrix_1)[rownames(correlation_matrix_1) == "jobsatT2"] <- "Job satisfaction(T2)"
rownames(correlation_matrix_1)[rownames(correlation_matrix_1) == "FWDfwagency"] <- "Belief in free will(T1)"
rownames(correlation_matrix_1)[rownames(correlation_matrix_1) == "jobautT1"] <- "Job autonomy(T1)"
rownames(correlation_matrix_1)[rownames(correlation_matrix_1) == "jobautT2"] <- "Job autonomy(T2)"
rownames(correlation_matrix_1)[rownames(correlation_matrix_1) == "locus"] <- "Trait locus of control(T1)"
rownames(correlation_matrix_1)[rownames(correlation_matrix_1) == "ess_kind"] <- "Implicit beliefs(T1)"
rownames(correlation_matrix_1)[rownames(correlation_matrix_1) == "selfest"] <- "Trait self-esteem(T1)"
rownames(correlation_matrix_1)[rownames(correlation_matrix_1) == "selfeff"] <- "Job self-efficacy(T1)"
rownames(correlation_matrix_1)[rownames(correlation_matrix_1) == "selfcontrol"] <- "Trait self-control(T1)"

correlation_matrix_1[1,3] <- paste("(" ,alphas1[1],")")
correlation_matrix_1[2,4] <- paste("(" ,alphas1[2],")")
correlation_matrix_1[3,5] <- paste("(" ,alphas1[3],")")
correlation_matrix_1[4,6] <- paste("(" ,alphas1[4],")")
correlation_matrix_1[5,7] <- paste("(" ,alphas1[5],")")
#correlation_matrix_1[7,7] <- paste(correlation_matrix_1[7,7],"+")

#print the table
kable(correlation_matrix_1, booktabs = TRUE) |>
  add_header_above(c(" " =1, " " = 1, " " = 1, "Job satisfaction" =1,"Job satisfaction" = 1,"Belief in free will" =1,"Job autonomy" =1,"Job autonomy" = 1),line=FALSE, align = "c") |>
  kable_styling(font_size = 6, position = "left")

```
*Note.* T1 = collected in Time 1 (n=209), T2 = collected in Time 2 (n = 137); diagonal values are reliability alpha coefficients. Scales in free will 1-6; Scales in job satisfaction, job autonomy, trait self-esteem, implicit beliefs 1-7; locus of control, 1-7; locus of control, 0-13; trait self-control, 1-5. 
+p<.10. \*p <.05. \*\*p<.01.\***p<.001.

# Discussion

## Detailed findings

The original paper by @feldman demonstrates that a strong belief in free will results in significant increases in job satisfaction; this correlation is relevant across cultural differences and in different work fields (e.g., from Taiwanese real estate agents to American digital labour) similar results were maintained.

Through this paper, we conducted a replication study on institutional beliefs in the digital gig economy (specifically the MTurk community) and sought to determine whether there is a positive relationship between U.S. workers’ beliefs about free will and their job satisfaction with Amazon Mechanical. Based on an analysis of information from a six-month focused study of Amazon MTurk workers presented and other related auxiliary analyses of different industries in the original paper, our results confirm a positive relationship, indicating that workers with a stronger belief in free will tend to report higher levels of job satisfaction. Our analysis shows that the correlation between free will beliefs and job satisfaction is more vital in this digital microtask environment than in a traditional work environment. The above reinforces the idea that institutional beliefs in the increasingly prevalent gig economy are not just philosophical abstractions but have real consequences for workforce well-being.

## Theoretical Implications

The findings from our study offer theoretical implications for understanding job satisfaction in the context of the gig economy. Specifically, they suggest that beliefs in free will play a crucial role in shaping workers' perceptions of their autonomy and, consequently, their job satisfaction. This challenges and extends traditional theories of job satisfaction by incorporating the psychological dimension of free will beliefs, especially in flexible work environments like MTurk. It invites a reevaluation of how autonomy is conceptualized and valued in non-traditional work settings, advocating for a broader understanding of factors contributing to job satisfaction. The result is it highlights the importance of creating an environment that enhances employee autonomy, potentially increasing employee engagement and satisfaction.

## Journal Study: Work and Freedom in the Context of Agency Beliefs and Job Satisfaction

To further confirm the validity of the original paper and our analysis, we selected another peer-reviewed professional academic journal for reference. By analyzing the comprehensive study conducted by @Baldissarri, we explored the complex relationship between work activities that trigger self-objectification and subsequent beliefs in personal free will. Through a series of methodologically rigorous studies, this research illustrates that diminished free will beliefs are a result of engaging in repetitive, fragmented, and externally directed tasks. This reduction in belief in free will, mediated by self-objectification, sets up a subtle interplay between the nature of work and the psychological makeup of the worker. Consistent with @feldman. @Baldissarri established a link between free will beliefs and job satisfaction. Further emphasis is placed on the complexity of agency within the professional realm.

Our findings suggest that MTurk employees (gig economy) who perceive greater autonomy and personal agency report greater job satisfaction, which resonates with the implications of the work of Baldissarri et al. Routine and piecemeal tasks on MTurk can lead to some form of self-objectification, potentially undermining belief in individual free will and, in turn, job satisfaction. Therefore, the inherent structure of gig work may require strategies that enhance perceptions of free will and personal agency to increase job satisfaction.

## Ethical Considerations in Long-Term Behavioural Studies

Ethical considerations are crucial in long-term behavioural research, especially when studying beliefs and job satisfaction. In doing so, we focused on the research methods and ethical concerns of the original academic journal [@feldman]. @feldman took a series of steps to ensure the ethics of the study, including ensuring informed consent, protecting privacy and data security, and providing long-term participant support and opportunities for explanation.

We agree with the above ethically appropriate measures of the original academic journal and believe that the research paid particular attention to avoiding any possible adverse psychological effects and ensured that all research standards were met through ethical oversight by the institutional review board. This approach ensures maximum protection of participant well-being during the research process and reinforces our commitment to ethical standards while also improving research quality and participant trust in the research.

## Accounting for Bias

In addressing bias within the discussion section of our paper, it's essential to acknowledge that while our study expands on the foundational research by @feldman in exploring the impact of free will beliefs on job satisfaction, particularly within the digital gig economy of Amazon Mechanical Turk, inherent biases in data collection and analysis could influence the outcomes. Ethical implications and biases naturally emerge in both quantitative and qualitative research. For instance, sampling bias can occur when the study participants are not representative of the broader population intended to be analyzed. This type of bias might be mitigated through strategies such as simple random sampling, ensuring that every individual within the target population has an equal chance of selection. However, challenges such as self-selection bias, where individuals with a strong interest in the topic may be more likely to participate, can skew results. Despite efforts to create a representative sample through demographic balancing, such biases may persist, potentially limiting the generalizability of the findings. Thus, acknowledging these limitations and adopting rigorous methodological safeguards are crucial for enhancing the credibility and applicability of research conclusions.

## Analytical Limitations

While our study sheds light on the relationship between free will beliefs and job satisfaction in the context of MTurk, it also highlights several limitations. The unique demographics of MTurk workers and the platform's specific work conditions may not fully extrapolate to the broader gig economy. For instance, platforms like MTurk offer a degree of autonomy by allowing workers to choose tasks; however, this freedom is within the confines of predetermined task parameters and compensation set by the platform.

Upon revisiting the original paper by @feldman, we have identified certain unclear in the correlation coefficients about the variable `Beliefs in Free Will (T1)` in @tbl-Means-SD-Corr and @tbl-demo-corr. Unlike other variables used for the tables, the 'Beliefs in Free Will (T1)' components are not explicitly defined in the original paper and other supplementary documents. Such discrepancies could lead people replicating this paper to unclear definitions and calculation errors, thus necessitating a closer examination of the computational processes employed in the original study. Another variable, ' FW T1 All subscales combined' in @tbl-corr-between-subscales, has a similar problem.

In addition, in @tbl-corr-between-subscales, we found that the significance label is more robust, where the p-value is smaller (<. 001) compared to the original paper (<.01). The difference could result from differences between statistical tools we used for the analysis (R versus SPS).

## Future Research Pathways

In light of the above limitations, future research should explore this relationship across diverse gig platforms and investigate the longitudinal effects of free will beliefs on job satisfaction to establish the relation. Additionally, examining the interplay between personal autonomy and platform policies could offer insights into optimizing job satisfaction in gig work.

To address these concerns in some unclear variables in correlation coefficients, we recommend thoroughly re-evaluating the data computation methods used, including a detailed review of the data transformation steps described by @feldman. Enhanced validation procedures and sensitivity analyses will be instrumental in clarifying these differences. This approach will bolster the credibility of our replication study and contribute to the scientific community's ongoing efforts to refine research methodologies in the study of free will beliefs and their impact on job satisfaction.

A closer examination of the statistical tools and methodologies is essential to solve the observed differences in significance levels and p-values between our study and the original research. The discrepancy, particularly in the robustness of the significance label observed in correlation tables, suggests a variation in the statistical analysis approach due to the utilization of R in our study as opposed to SPSS in the original research. Therefore, future endeavours should involve a detailed comparison and calibration of analytical techniques across different statistical software to ensure consistency in findings.

Finally, we believe it is imperative to consider the potential of datasets like the one from Study 3, which presents a valuable opportunity for comprehensive analysis with its large sample size and cross-cultural scope. Unfortunately, this dataset was not made available in the original paper, leading us to focus our efforts on Study 2. Moving forward, we are particularly interested in leveraging such diverse, cross-cultural, and large-scale datasets to deepen our understanding of the impact of free will beliefs on job satisfaction across different global contexts. This approach promises to enrich our insights and enhance the generalizability of our findings, opening new avenues for investigation in the gig economy and beyond.

# Conclusion

In summary, our investigation based on the original paper from @feldman affirmed a strong positive link between the belief in free will and job satisfaction within the dynamic sphere of the gig economy, notably on Amazon's Mechanical Turk platform. Central to this relationship is the role of perceived autonomy, which significantly elevates job satisfaction levels. These findings underscore the importance of nurturing autonomy within gig work, advocating for a work environment that acknowledges and bolsters personal agency. As the gig economy continues to evolve, future research should delve into the broader application of these insights, aiming to enhance the well-being and job satisfaction of the diverse gig workforce.

\appendix

# Appendix {-}

## Study 1 Scale {#sec-study1}

The following questions were asked in Study 1, based on topic. (R) indicates a question that is reversed, wherein the most positive responses strongly disagree or disagree with the statement.

Free will

* I am in charge of the decisions I make.
* I actively choose what to do among the choices I have.
* I am in charge of my actions even when my life’s circumstances are difficult.
* My decisions are influenced by a higher power. (R)
* I have free will even when my choices are limited by external circumstances.
* I decide what action to take in a particular situation.
* My choices are limited because they fit into a larger plan. (R)
* I have free will.

Job satisfaction

* Generally speaking, I am very satisfied with my job.
* I am generally satisfied with the feeling of worthwhile accomplishment I get from doing this job.
* I am satisfied with the kind of work I do in this job.

## Study 2 Scale {#sec-study2}

The following questions were asked in Study 2, based on topic. (R) indicates a question that is reversed, wherein the most positive responses strongly disagree or disagree with the statement.

Job satisfaction
* I feel fairly well satisfied with my present job doing MTurk tasks
* Most days I am enthusiastic about the work I do on MTurk
* Every time I work on tasks on MTurk it feels like forever
* I find real enjoyment in the work I do on MTurk
* I consider the kind of work I do on MTurk rather unpleasant (reversed)

Job autonomy

* I have significant autonomy in determining how I do my job on MTurk
* I can decide on my own how to go about doing my work on MTurk
* I have considerable opportunity for independence and freedom in how I do my job on MTurk

Controls

* I am good at resisting temptation.
* I have a hard time breaking bad habits.
* I am lazy.
* I say inappropriate things. (R) 
* I do certain things that are bad for me, if they are fun. (R)
* I refuse things that are bad for me. 
* I wish I had more self-discipline. (R) 
* People would say that I have iron self- discipline.
* Pleasure and fun sometimes keep me from getting work done. (R) 
* I have trouble concentrating. (R) 
* I am able to work effectively toward long-term goals.
* Sometimes I can’t stop myself from doing something, even if I know it is wrong. (R)
* I often act without thinking through all the alternatives. (R)

Locus of Control

Please choose one choice (a or b) for each. Score one point for response ‘a’ to questions: 1, 3, 4, 5, 10, 11, 12, and 13.

* 1. 
+ a. Children get into trouble because their parents punish them too much. 
+ b. The trouble with most children nowadays is that their parents are too easy with them.
* 2. 
+ a. Many of the unhappy things in people's lives are partly due to bad luck. 
+ b. People's misfortunes result from the mistakes they make. 
* 3.
+ a. One of the major reasons why we have wars is because people don't take enough interest in politics. 
+ b. There will always be wars, no matter how hard people try to prevent them. 
* 4. 
+ a. In the long run people get the respect they deserve in this world. 
+ b. Unfortunately, an individual's worth often passes unrecognized no matter how hard he tries. 
* 5. 
+ a. The idea that teachers are unfair to students is nonsense. 
+ b. Most students don't realize the extent to which their grades are influenced by accidental happenings. 
* 6. 
+ a. Without the right breaks, one cannot be an effective leader. 
+ b. Capable people who fail to become leaders have not taken advantage of their opportunities. 
* 7. 
+ a. No matter how hard you try, some people just don't like you. 
+ b. People who can't get others to like them don't understand how to get along with others.
* 8. 
+ a. Heredity plays the major role in determining one's personality. 
+ b. It is one's experiences in life which determine what they're like.
* 9. 
+ a. I have often found that what is going to happen will happen. 
+ b. Trusting fate has never turned out as well for me as making a decision to take a definite course of action. 
* 10. 
+ a. In the case of the well prepared student there is rarely, if ever, such a thing as an unfair test. 
+ b. Many times, exam questions tend to be so unrelated to course work that studying is really useless.
* 11.
+ a. Becoming a success is a matter of hard work, luck has little or nothing to do with it. 
+ b. Getting a good job depends mainly on being in the right place at the right time. 
* 12. 
+ a. The average citizen can have an influence in government decisions. 
+ b. This world is run by the few people in power, and there is not much the little guy can do about it.
* 13. 
+ a. When I make plans, I am almost certain that I can make them work. 
+ b. It is not always wise to plan too far ahead because many things turn out to be a matter of good or bad fortune anyhow.

Self-esteem

* I feel that I am a person of worth, at least on an equal basis with others.
* I feel that I have a number of good qualities.
* All in all, I am inclined to feel that I am a failure.
* I am able to do things as well as most other people. 
* I feel that I do not have much to be proud of. (R)
* I take a positive attitude toward myself. 
* On the whole, I am satisfied with myself. 
* I wish I could have more respect for myself. (R) 
* I certainly feel useless at times. (R) 
* At times I think I am no good at all. (R)

Self-efficacy

* I am strong enough to overcome life's struggles.
* At root, I am a weak person.
* I can handle the situations that life brings.
* I usually feel that I am an unsuccessful person. (R) 
* I often feel that there is nothing that I can do well. (R) 
* I feel competent to deal effectively with the real world. 
* I often feel like a failure. (R) 
* I usually feel I can handle the typical problems that come up in life.

## Study 3 Scale {#sec-study3}

* Indicate how much freedom of choice and control you feel you have over the way
your life turns out (1 = No choice and control to 10 = A great deal of choice and control)
* Overall, how satisfied or dissatisfied are you with your job? (1 = Dissatisfied to 10 =
Satisfied).
* How free are you to make decisions in your job? (1 = None at all to 10 = A great deal)

\newpage
# References

### 2024-03-11 scripts/00-simulate_data.R

@@ -1,0 +1,27 @@
+#### Preamble ####
+# Purpose: Simulate the dataset for code testing
+# Author: Mingjia Chen, Hadi Ahmad, Tianen (Evan) Hao
+# Date: 17 February 2024 
+# Contact: mingjia.chen@mail.utoronto.ca 
+# License: MIT
+# Pre-requisites: none
+
+
+#### Workspace setup ####
+library(tidyverse)
+
+
+#### Simulate data ####
+set.seed(114514)
+num_observations = 100
+
+simulated_data <-
+  tibble(
+    fw_belief =  runif(n = num_observations, min = 1, max = 6) |> round(),
+    jobsat = runif(n = num_observations, min = 1, max = 7) |> round(),
+    jobaut = runif(n=num_observations, min=1, max = 7) |> round(),
+    fwdPower =  runif(n = num_observations, min = 1, max = 6) |> round(),
+    fwdSelf = runif(n = num_observations, min = 1, max = 7) |> round(),
+    age = runif(n=num_observations, min=12, max = 60) |> round(),
+    gender = runif(n=num_observations, min=0, max = 1) |> round()
+  )

### 2024-03-11 scripts/01-download_data.R

@@ -1,0 +1,11 @@
+#### Preamble ####
+# Purpose: Dataset Downloading for research
+# Author: Mingjia Chen, Hadi Ahmad, Tianen (Evan) Hao
+# Date: 17 February 2024 
+# Contact: mingjia.chen@mail.utoronto.ca 
+# License: MIT
+# Pre-requisites: none
+
+
+# The download of the raw data requires sign-in to Open Science Framework (OSF) website (https://osf.io/d2e6s/). 
+# The whole replication package is avaliable on site for downloading.

### 2024-03-11 scripts/02-data_cleaning.R

@@ -1,0 +1,314 @@
+#### Preamble ####
+# Purpose: Clean Study 2 Dataset
+# Author: Mingjia Chen, Hadi Ahmad, Tianen (Evan) Hao
+# Date: 11 February 2024
+# Contact: mingjia.chen@mail.utoronto.ca 
+# License: MIT
+# Pre-requisites: R 4.3.2
+
+#### Workspace setup ####
+library(tidyverse)
+library(dplyr)
+library(haven)
+
+#### Clean data ####
+data <- read_sav("inputs/data/FW satisfaction-Study 2-data.sav")
+
+data <- mutate(data,
+               jobsat_3r = case_when(
+                 jobsat_3 == 1 ~ 7,
+                 jobsat_3 == 2 ~ 6,
+                 jobsat_3 == 3 ~ 5,
+                 jobsat_3 == 4 ~ 4,
+                 jobsat_3 == 5 ~ 3,
+                 jobsat_3 == 6 ~ 2,
+                 jobsat_3 == 7 ~ 1,
+                 TRUE ~ jobsat_3
+               ),
+               jobsat_5r = case_when(
+                 jobsat_5 == 1 ~ 7,
+                 jobsat_5 == 2 ~ 6,
+                 jobsat_5 == 3 ~ 5,
+                 jobsat_5 == 4 ~ 4,
+                 jobsat_5 == 5 ~ 3,
+                 jobsat_5 == 6 ~ 2,
+                 jobsat_5 == 7 ~ 1,
+                 TRUE ~ jobsat_5
+               ),
+               jobsat2_3r = case_when(
+                 jobsat2_3 == 1 ~ 7,
+                 jobsat2_3 == 2 ~ 6,
+                 jobsat2_3 == 3 ~ 5,
+                 jobsat2_3 == 4 ~ 4,
+                 jobsat2_3 == 5 ~ 3,
+                 jobsat2_3 == 6 ~ 2,
+                 jobsat2_3 == 7 ~ 1,
+                 TRUE ~ jobsat2_3
+               ),
+               jobsat2_5r = case_when(
+                 jobsat2_5 == 1 ~ 7,
+                 jobsat2_5 == 2 ~ 6,
+                 jobsat2_5 == 3 ~ 5,
+                 jobsat2_5 == 4 ~ 4,
+                 jobsat2_5 == 5 ~ 3,
+                 jobsat2_5 == 6 ~ 2,
+                 jobsat2_5 == 7 ~ 1,
[…]

### 2024-03-11 scripts/03-data_tabling.R

@@ -1,0 +1,113 @@
+#### Preamble ####
+# Purpose: Study 2 Table Creating
+# Author: Mingjia Chen, Hadi Ahmad, Tianen (Evan) Hao
+# Date: 17 February 2024
+# Contact: mingjia.chen@mail.utoronto.ca 
+# License: MIT
+# Pre-requisites: R 4.3.2
+
+#download the packages if necessary, then load the packages
+if (!require("pacman")) install.packages("pacman")
+pacman::p_load(haven, psych,dplyr,tidyverse, knitr,kableExtra)
+
+# Load the psych package
+library(psych)
+library(dplyr)
+library(tidyverse)
+library(knitr)
+
+data <- read_csv("FW_satisfaction-Study_2-data.csv")
+
+##### Table 1. Study 2 Means, Standard Deviations, and Correlations################################################################################
+# Select the variables for correlation analysis
+selected_variables <-data[, c("jobsat1", "jobsat2", "FWDfwagency", "jobaut", "jobaut2", "locus", "ess_kind", "selfest", "selfeff", "selfcontrol")]
+
+# Compute pairwise correlations
+correlation_matrix <- cor(selected_variables, use = "pairwise.complete.obs")
+
+# modifying the format so it matches to the correlation table like in paper
+## making the upper right part zero
+
+## Add Mean and SD
+M <- c(mean(selected_variables$jobsat1), mean(selected_variables$jobsat2,na.rm = TRUE), mean(selected_variables$FWDfwagency),
+       mean(selected_variables$jobaut,na.rm = TRUE),mean(selected_variables$jobaut2,na.rm = TRUE),mean(selected_variables$locus),
+       mean(selected_variables$ess_kind),mean(selected_variables$selfest),mean(selected_variables$selfeff),
+       mean(selected_variables$selfcontrol))
+
+SD <- c(sd(selected_variables$jobsat1), sd(selected_variables$jobsat2,na.rm = TRUE), sd(selected_variables$FWDfwagency),
+       sd(selected_variables$jobaut,na.rm = TRUE),sd(selected_variables$jobaut2,na.rm = TRUE),sd(selected_variables$locus),
+       sd(selected_variables$ess_kind),sd(selected_variables$selfest),sd(selected_variables$selfeff),
+       sd(selected_variables$selfcontrol))
+
+#choose desired rows
[…]

### 2024-03-11 scripts/04-test_data.R

@@ -1,0 +1,25 @@
+#### Preamble ####
+# Purpose: Basic tests codes for dataset.
+# Author: Mingjia Chen, Hadi Ahmad, Tianen (Evan) Hao
+# Date: 17 February 2024 
+# Contact: mingjia.chen@mail.utoronto.ca 
+# License: MIT
+# Pre-requisites: 
+  # 00-simulate_data.R
+  # 01-data_cleaning.R
+
+#### Workspace setup ####
+library(tidyverse)
+
+#### Test data ####
+
+data$gender|>
+  unique() == c(0, 1)
+
+data$fw_belief |>
+  unique() |> length() ==6
+
+data$age|> min() >= 12
+data$year |> max() <= 60
+
+data$jobsat|> class() == "numeric"

### 2024-03-11 original_paper/Data_and_code/Mini_meta/minimetacor.R
Delete original_paper directory

@@ -1,69 +1,0 @@
-# mini meta analyses correlations functions
-
-
-# Installing all the required packages for this analysis (if not already installed)
-list.of.packages <- c("car", "foreign", "metafor", "Hmisc", "pequod", "openxlsx", "readxl")
-
-new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
-if(length(new.packages)) install.packages(new.packages, dependencies = TRUE)
-
-lapply(list.of.packages, library, character.only = TRUE)
-
-
-PrintMetaResult  <- function (metadataframe) {
-  print(summary(metadataframe))
-
-}
-
-PrintPlotMetaR  <- function (metadataframe) {
-  forest(metadataframe, xlab="Correlation", alim=c(-1,1))
-}
-
-PrintFunnelMetaR  <- function (metadataframe) {
-
-  
-  funnel(metadataframe,
-         level=0.95, 
-         xlim=c(-1,1))
-  legend(-.6, 0.0,
-         c("0.1 > p > 0.05", "0.05 > p > 0.01", "< 0.01"),
-         fill=c("darkgrey", "grey", "lightgrey"))
-  
-}
-
-CorMeta <- function (Correlation, SampleSize, StudyName) {
-
-  set.seed(513131)
-  dat <- escalc(measure = "COR", ri = Correlation, ni = SampleSize, append = TRUE)
-  mod <- rma(Correlation, vi, method = "REML", data = dat)
-  
-  return (mod)
-}
-
-CorMetaES <- function (Correlation, SampleSize, StudyName) {
-
-  set.seed(513131)
-  dat <- escalc(measure = "COR", ri = Correlation, ni = SampleSize, append = TRUE)
-  mod <- rma(Correlation, vi, method = "REML", data = dat)
-  
-  return (mod$b[1])
-}
-
-CorMetaESlow <- function (Correlation, SampleSize, StudyName) {
-  
-  set.seed(513131)
-  dat <- escalc(measure = "COR", ri = Correlation, ni = SampleSize, append = TRUE)
-  mod <- rma(Correlation, vi, method = "REML", data = dat)
-  
-  return (mod$ci.lb)
-}
-
-CorMetaEShigh <- function (Correlation, SampleSize, StudyName) {
-  
-  set.seed(513131)
-  dat <- escalc(measure = "COR", ri = Correlation, ni = SampleSize, append = TRUE)
[…]

### 2024-03-11 original_paper/Data_and_code/Mini_meta/running-meta-r-correlational-syntax.R

@@ -1,30 +1,0 @@
-# this.dir <- dirname(rstudioapi::getActiveDocumentContext()$path)
-# setwd(this.dir)
-source("minimetacor.R")
-
-idataset1 <- read.table("summary-time1.csv", header=TRUE, sep=",", na.strings="NA", dec=".", strip.white=TRUE)
-str(idataset1)
-idataset1$Study
-
-odataset1<-CorMeta(idataset1$R, idataset1$N,idataset1$Study)
-str(odataset1)
-PrintMetaResult(odataset1)
-PrintPlotMetaR(odataset1)
-PrintFunnelMetaR(odataset1)
-predict(odataset1)
-confint(odataset1)
-baujat(odataset1)
-
-idataset2 <- read.table("summary-time2.csv", header=TRUE, sep=",", na.strings="NA", dec=".", strip.white=TRUE)
-str(idataset2)
-idataset2$Study
-
-odataset2<-CorMeta(idataset2$R, idataset2$N,idataset2$Study)
-str(odataset2)
-PrintMetaResult(odataset2)
-PrintPlotMetaR(odataset2)
-PrintFunnelMetaR(odataset2)
-predict(odataset2)
-confint(odataset2)
-baujat(odataset2)
-

### 2024-03-11 scripts/01-download_data.R
Update downloading data

@@ -1,11 +1,11 @@
 #### Preamble ####
 # Purpose: Dataset Downloading for research
-# Author: Mingjia Chen, Hadi Ahmad, Tianen (Evan) Hao
-# Date: 17 February 2024 
+# Author: Mingjia Chen, Catherine Punnoose, Tianen (Evan) Hao
+# Date: 11 March 2024 
 # Contact: mingjia.chen@mail.utoronto.ca 
 # License: MIT
 # Pre-requisites: none
 
 
-# The download of the raw data requires sign-in to Open Science Framework (OSF) website (https://osf.io/d2e6s/). 
-# The whole replication package is avaliable on site for downloading.
+# The download of the raw data requires filtering and browsing The General Social Survey (https://gss.norc.org/documents/stata/GSS_stata.zip). 
+# The whole replication package is available on-site for downloading regarding to the GSS Codebook.

### 2024-03-11 scripts/02-data_cleaning.R
Update data cleaning

@@ -1,314 +1,118 @@
 #### Preamble ####
-# Purpose: Clean Study 2 Dataset
-# Author: Mingjia Chen, Hadi Ahmad, Tianen (Evan) Hao
-# Date: 11 February 2024
+# Purpose: Clean GSS Dataset
+# Author: Mingjia Chen, Catherine Punnoose, Tianen (Evan) Hao
+# Date: 11 March 2024 
 # Contact: mingjia.chen@mail.utoronto.ca 
 # License: MIT
-# Pre-requisites: R 4.3.2
+# Pre-requisites: R 4.3.2, Cropped_Data.csv
 
 #### Workspace setup ####
+library(janitor)
 library(tidyverse)
+library(knitr)
 library(dplyr)
-library(haven)
+library(kableExtra)
+library(here)
 
 #### Clean data ####
-data <- read_sav("inputs/data/FW satisfaction-Study 2-data.sav")
+# load dataset that has been cropped for analysis
+data <- read.csv(here::here("/inputs/data/Cropped_Data.csv"))
 
-data <- mutate(data,
-               jobsat_3r = case_when(
-                 jobsat_3 == 1 ~ 7,
-                 jobsat_3 == 2 ~ 6,
-                 jobsat_3 == 3 ~ 5,
-                 jobsat_3 == 4 ~ 4,
-                 jobsat_3 == 5 ~ 3,
-                 jobsat_3 == 6 ~ 2,
-                 jobsat_3 == 7 ~ 1,
-                 TRUE ~ jobsat_3
-               ),
-               jobsat_5r = case_when(
-                 jobsat_5 == 1 ~ 7,
-                 jobsat_5 == 2 ~ 6,
-                 jobsat_5 == 3 ~ 5,
-                 jobsat_5 == 4 ~ 4,
-                 jobsat_5 == 5 ~ 3,
-                 jobsat_5 == 6 ~ 2,
-                 jobsat_5 == 7 ~ 1,
-                 TRUE ~ jobsat_5
-               ),
-               jobsat2_3r = case_when(
-                 jobsat2_3 == 1 ~ 7,
-                 jobsat2_3 == 2 ~ 6,
-                 jobsat2_3 == 3 ~ 5,
-                 jobsat2_3 == 4 ~ 4,
-                 jobsat2_3 == 5 ~ 3,
-                 jobsat2_3 == 6 ~ 2,
-                 jobsat2_3 == 7 ~ 1,
[…]

### 2024-03-11 scripts/03-data_tabling.R
Update data_tabling

@@ -1,113 +1,188 @@
 #### Preamble ####
-# Purpose: Study 2 Table Creating
-# Author: Mingjia Chen, Hadi Ahmad, Tianen (Evan) Hao
-# Date: 17 February 2024
+# Purpose: GSS Tables and Graphs for the Paper
+# Author: Mingjia Chen, Catherine Punnoose, Tianen (Evan) Hao
+# Date: 11 March 2024 
 # Contact: mingjia.chen@mail.utoronto.ca 
 # License: MIT
-# Pre-requisites: R 4.3.2
+# Pre-requisites: R 4.3.2, Cropped_Data.csv, cleaned_categorized_data.csv
 
 #download the packages if necessary, then load the packages
 if (!require("pacman")) install.packages("pacman")
-pacman::p_load(haven, psych,dplyr,tidyverse, knitr,kableExtra)
+pacman::p_load(janitor,here,dplyr,tidyverse,knitr,kableExtra,ggplot2)
 
 # Load the psych package
-library(psych)
-library(dplyr)
+library(janitor)
 library(tidyverse)
 library(knitr)
+library(dplyr)
+library(kableExtra)
+library(here)
+library(ggplot2)
 
-data <- read_csv("FW_satisfaction-Study_2-data.csv")
+# Overview of the Categorized Data 
+data <- read.csv(here:here("/input/data/cleaned_categorized_data.csv"))
+# Delete the column
+data <- data[c(2:ncol(data))]
+colnames(data)[1] <- "Work Hours/Years"
+# Get rid of the first letter X for each of the years
+colnames(data) <- gsub("X", "", colnames(data))
 
-##### Table 1. Study 2 Means, Standard Deviations, and Correlations################################################################################
-# Select the variables for correlation analysis
-selected_variables <-data[, c("jobsat1", "jobsat2", "FWDfwagency", "jobaut", "jobaut2", "locus", "ess_kind", "selfest", "selfeff", "selfcontrol")]
+data_selected <- data[c("Work Hours/Years", "1998","2008","2021","Total")]
+kable(data_selected,row.names = FALSE)|>
+  kable_styling() |>
+  row_spec(6, hline_after = TRUE)
 
-# Compute pairwise correlations
-correlation_matrix <- cor(selected_variables, use = "pairwise.complete.obs")
+# Overview of the 1998 Survey Data 
+data <- read.csv(here:here("/input/data/cleaned_categorized_data.csv"))
[…]

### 2024-03-12 scripts/00-simulate_data.R
Update simulate_data

@@ -1,27 +1,35 @@
 #### Preamble ####
-# Purpose: Simulate the dataset for code testing
-# Author: Mingjia Chen, Hadi Ahmad, Tianen (Evan) Hao
-# Date: 17 February 2024 
+# Purpose:  Simulate the dataset for code testing
+# Author: Mingjia Chen, Catherine Punnoose, Tianen (Evan) Hao
+# Date: 11 March 2024 
 # Contact: mingjia.chen@mail.utoronto.ca 
 # License: MIT
 # Pre-requisites: none
 
-
 #### Workspace setup ####
-library(tidyverse)
+library(tibble)
+library(dplyr)
 
 
 #### Simulate data ####
-set.seed(114514)
-num_observations = 100
+# Define years and work hours categories
+years <- c(1972, 1973, 1974, 1975, 1976, 1977, 1978, 1980, 1981, 1982, 1983, 1984, 1985, 1986, 1987, 1988, 1989, 1990, 1991, 1992, 1993, 1994, 1995, 1996, 1997, 1998, 1999, 2000, 2001, 2002, 2003, 2004, 2005, 2006, 2008, 2010, 2012, 2014, 2016, 2018, 2021, 2022)
+work_hours_categories <- c("No Response", "0-20", "21-40", "41-60", "61-80")
 
-simulated_data <-
-  tibble(
-    fw_belief =  runif(n = num_observations, min = 1, max = 6) |> round(),
-    jobsat = runif(n = num_observations, min = 1, max = 7) |> round(),
-    jobaut = runif(n=num_observations, min=1, max = 7) |> round(),
-    fwdPower =  runif(n = num_observations, min = 1, max = 6) |> round(),
-    fwdSelf = runif(n = num_observations, min = 1, max = 7) |> round(),
-    age = runif(n=num_observations, min=12, max = 60) |> round(),
-    gender = runif(n=num_observations, min=0, max = 1) |> round()
-  )
+# Create the initial tibble with work_hours column
+simulated_data <- tibble(work_hours = work_hours_categories)
+
+# Add each year as a new column with simulated data
+set.seed(123) # For reproducibility
+for(year in years) {
+  simulated_data[[as.character(year)]] <- runif(n = length(work_hours_categories), min = 50, max = 2000)
+}
+
+# Correct test for a specific year's range of values using appropriate column referencing
+test_year_range <- all(simulated_data[["2022"]] >= 50 & simulated_data[["2022"]] <= 2000)
[…]

### 2024-03-12 scripts/04-test_data.R
Updated test_data

@@ -1,7 +1,7 @@
 #### Preamble ####
 # Purpose: Basic tests codes for dataset.
-# Author: Mingjia Chen, Hadi Ahmad, Tianen (Evan) Hao
-# Date: 17 February 2024 
+# Author: Mingjia Chen, Catherine Punnoose, Tianen (Evan) Hao
+# Date: 11 March 2024 
 # Contact: mingjia.chen@mail.utoronto.ca 
 # License: MIT
 # Pre-requisites: 
@@ -9,17 +9,38 @@
   # 01-data_cleaning.R
 
 #### Workspace setup ####
-library(tidyverse)
+library(dplyr)
 
 #### Test data ####
+data <- read.csv(here:here("/inputs/data/cleaned_categorized_data.csv"))
+test_non_negative <- all(select(data, -work_hours) >= 0)
+print(test_non_negative)
+#The result shows that the year columns does not contain non-negative values.
 
-data$gender|>
-  unique() == c(0, 1)
+# 2. Verify that Work Hours Categories Match Expected Set 
+#Checks if the work_hours categories exactly match a predefined list.
+expected_categories <- c("No Response", "0-20", "21-40", "41-60", "61-80","80+","Total")
+test_categories_match <- all(data$work_hours %in% expected_categories)
+print(test_categories_match)
+#We do have these categories, indicating that our cleaning is successful.
 
-data$fw_belief |>
-  unique() |> length() ==6
+# 3. Confirm No Missing Values in Year Columns
+#Confirms there are no NA values in the columns representing years.
+test_no_missing_values <- all(!is.na(select(data, -work_hours)))
+print(test_no_missing_values)
+#We do not have missing values in year columns, meaning that we did not lose
+#data during the process of cleaning.
 
-data$age|> min() >= 12
-data$year |> max() <= 60
+# 4. Check for a Specific Year's Range of Values
+# Verifies that the values for a specific year fall within an expected range.
+test_year_range <- all(data$`2022` >= 50 & data$`2022` <= 2000)
+print(test_year_range)
+#The data still falls in the range, meaning no outstanding number errors after
+#the process the cleaning.
 
-data$jobsat|> class() == "numeric"
+# 5. Check for Consistency in Data Types
+#Ensures that the data type for the year columns is integer, as expected from the simulation setup.
+test_data_types <- all(sapply(data[,-c(1,2)], is.integer))
+print(test_data_types)
+#The data is consistent as everything except working hours are integers.
+

### 2024-03-12 scripts/02-data_cleaning.R
Update data_cleaning

@@ -115,4 +115,4 @@ cate_data <- rbind(No_Response,tweenties,forties,sixties,eighties,more,total)
 cate_data <- data.frame(cbind(Hours,cate_data))
 colnames(cate_data) <- year
 
-write.csv(cate_data,""/inputs/data/cleaned_categorized_data.csv")
+write.csv(cate_data,"/inputs/data/cleaned_categorized_data.csv")

### 2024-03-12 outputs/paper/paper.qmd
update data and paper

---
title: "Labour Market Resilience"
subtitle: "Economic Crisis Has Diverse Impacts on Industry Work Hours"
author: 
  - Mingjia Chen
  - Catherine Punnoose
  - Tianen (Evan) Hao
thanks: "Code and data are available at: https://github.com/ShadyEvan4830/Labour_Market_Resilience.git"
date: March 11, 2024
date-format: long
abstract: "First sentence, second sentence, third sentence."
format: pdf
toc: true
number-sections: true
bibliography: bibliography.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

#download the packages if necessary, then load the packages
if (!require("pacman")) install.packages("pacman")
pacman::p_load(janitor,here,dplyr,tidyverse,knitr,kableExtra,ggplot2)

library(janitor)
library(tidyverse)
library(knitr)
library(dplyr)
library(kableExtra)
library(here)
library(ggplot2)
```

# Introduction

# Data

## Source Data

For the analysis, we retrieved the following data as described in @tbl-use-var.

| Variable | New Name   | Description                     | Example |
|----------|------------|---------------------------------|---------|
| response | work hours | Respondent's response           | 23      |
| year     | year       | The year of the survey recorded | 2007    |

: Source data retrieved from GSS {#tbl-use-var}

## Data Cleaning

The data was downloaded and filtered for the selected variables from the selected data variables from GSS[^1]. The data cleaning was performed based on value definitions as defined in the GSS codebook [@gssCodebook]. One of the variable names `response` is renamed to be more informative [@tbl-use-var].

The data was thus been cleaned by using the open source statistically programming language R [@citeR], with libraries `tidyverse` [@tidyverse], `ggplot2` [@ggplot2], `dplyr` [@dplyr], `readr` [@readr], `tibble` [@tibble], `here` [@here], `kableExtra` [@kableExtra], `janitor` [@janitor], and `knitr` [@knitr].

[^1]: https://gss.norc.org/documents/stata/GSS_stata.zip

```{r}
#| label: tbl-data-overview
#| tbl-cap: Overview of the Categorized Data 
#| echo: false
#| warning: false
#| message: false

data <- read.csv(here::here("inputs/data/cleaned_categorized_data.csv"))
# Delete the column
data <- data[c(2:ncol(data))]
colnames(data)[1] <- "Work Hours/Years"
# Get rid of the first letter X for each of the years
colnames(data) <- gsub("X", "", colnames(data))

data_selected <- data[c("Work Hours/Years", "1998","2008","2021","Total")]
kable(data_selected,row.names = FALSE)|>
  kable_styling() |>
  row_spec(6, hline_after = TRUE)
```

## Data Limitations

## Survey Methodology

### 1998 Survey Methodology 
```{r}
#| label: fig-Survey-1998
#| tbl-cap: Overview of the 1998 Survey Data 
#| echo: false
#| warning: false
#| message: false
data <- read.csv(here::here("inputs/data/cleaned_categorized_data.csv"))
data <- data[1:6,]

ggplot(data, aes(x = "", y = X1998, fill = work_hours)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar("y", start = 0) +
  scale_fill_brewer(palette = "Set3") +  # Use a color palette
  theme_void() +  # Remove background and gridlines
  labs(title = "1998 Survey Results") +
  theme(plot.title = element_text(hjust = 0.5, size = 16))
```
\break

### 2008 Survey Methodology

```{r}
#| label: fig-Survey-2008
#| tbl-cap: Overview of the 2008 Survey Data 
#| echo: false
#| warning: false
#| message: false

data <-read.csv(here::here("inputs/data/cleaned_categorized_data.csv"))
data <- data[1:6,]

ggplot(data, aes(x = "", y = X2008, fill = work_hours)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar("y", start = 0) +
  scale_fill_brewer(palette = "Set3") +  # Use a color palette
  theme_void() +  # Remove background and gridlines
  labs(title = "2008 Survey Results") +
  theme(plot.title = element_text(hjust = 0.5, size = 16))
```
\break

### Gap in 2020 Data 
```{r}
#| label: fig-Survey-2021
#| tbl-cap: Overview of the 2021 Survey Data 
#| echo: false
#| warning: false
#| message: false
data <- read.csv(here::here("inputs/data/cleaned_categorized_data.csv"))
data <- data[1:6,]

ggplot(data, aes(x = "", y = X2021, fill = work_hours)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar("y", start = 0) +
  scale_fill_brewer(palette = "Set3") +  # Use a color palette
  theme_void() +  # Remove background and gridlines
  labs(title = "2021 Survey Results") +
  theme(plot.title = element_text(hjust = 0.5, size = 16))
```

### Non-responses

# Results

## Working Hour Comparison Between Financial Events

```{r}
#| label: fig-ave-hour-comparison
#| fig-cap: Average Working Hours Comparison between Financial Events
#| echo: false
#| warning: false
#| message: false

data <- read.csv(here::here("inputs/data/Cleaned_Data.csv"))
# Get rid of the first letter X for each of the years
colnames(data)[1] <- "work_hours"
colnames(data) <- gsub("X", "", colnames(data))

#Histogram of average working hours for 2008, 2021, 2022, and Total
hist_data <- select(data, work_hours,"2010","2018","2021")
hist_data <- hist_data[5:94,]

num <- 3 #number of years
sum <- rep(0,num)
total_people <- rep(0,num)
for(i in 1:num){
  total_people[i] <- sum(hist_data[, i+1])
}
hist_data[, 1] <- sapply(hist_data[, 1], as.numeric)
hist_data[90,1] <- 90

sum[1] <- sum(hist_data$"2010" * hist_data$work_hours)
sum[2] <- sum(hist_data$"2018" * hist_data$work_hours)
sum[3] <- sum(hist_data$"2021" * hist_data$work_hours)

averages <- round(sum/total_people) 
years <- c("2010","2018","2021")

average_hours <- data.frame(cbind(averages,years))

ggplot(average_hours,aes(x=years,y=averages)) +
  geom_bar(stat="identity") + 
  theme_minimal() + # Make the theme neater
  labs(x = "Year", y = "Average Working Hour") +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom")
```

\break

```{r}
#| label: fig-cate-comparisons
#| fig-cap: Categorical Working Hour Comparison between the Years
#| fig-subcap: ["Asian Financial Crisis (1998)","World Financial Crisis(2008)","During Covid-19 Pandemic (2021)", "Total"]
#| layout-ncol: 2
#| echo: false
#| warning: false
#| message: false

#still need to modify the graphs

data <- read.csv(here::here("inputs/data/cleaned_categorized_data.csv"))
data <- data[c(2:ncol(data))]
# Get rid of the first letter X for each of the years
colnames(data) <- gsub("X", "", colnames(data))

Data_1998 <- select(data,work_hours,`1998`)
ggplot(Data_1998,aes(x=work_hours,y=`1998`)) +
  geom_bar(stat="identity") + 
  theme_minimal() + # Make the theme neater
  labs(x = "Working Hours", y = "Number of Reports") +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom")

Data_2008 <- select(data,work_hours,`2008`)
ggplot(Data_2008,aes(x=work_hours,y=`2008`)) +
  geom_bar(stat="identity") + 
  theme_minimal() + # Make the theme neater
  labs(x = "Working Hours", y = "Number of Reports") +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom")

Data_2021 <- select(data,work_hours,`2021`)
ggplot(Data_2021,aes(x=work_hours,y=`2021`)) +
  geom_bar(stat="identity") + 
  theme_minimal() + # Make the theme neater
  labs(x = "Working Hours", y = "Number of Reports") +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom")

Data_Total <- select(data,work_hours,Total)
ggplot(Data_Total,aes(x=work_hours,y= Total)) +
  geom_bar(stat="identity") + 
  theme_minimal() + # Make the theme neater
  labs(x = "Working Hours", y = "Number of Reports") +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom")
```

\break

## Nonreponse Rate
```{r}
#| label: fig-nonresponse-rate
#| fig-cap: Nonresponse Rates
#| echo: false
#| warning: false
#| message: false

# Calculate percentages
data <- read.csv(here::here("inputs/data/cleaned_categorized_data.csv"))
data <- data[c(2:ncol(data))]
data <- data[1:6,]

#colnames(data) <- paste(colnames(data),"Year",sep="_")

colnames(data)<- as.character(colnames(data))

#data_long <- data %>% 
#  pivot_longer(cols = everything(), names_to = "WorkHours", values_to #= "Response")

# Select the 'No Response' row and remove the first column which is not needed for the plot
no_response_data <- data[data$work_hours == 'No Response', -1]

# We also need to remove the 'Total' column as we did in the Python example
no_response_data <- no_response_data[-length(no_response_data)]

# Calculate total responses per year excluding the 'work_hours' and 'Total' columns

data <- read.csv(here::here("inputs/data/cleaned_categorized_data.csv"))
data <- data[c(3:ncol(data))]

total_responses_per_year <- as.vector(data[7,])
total_responses_per_year <- unlist(total_responses_per_year)

# Calculate non-response rate as a percentage
non_response_rate <- (no_response_data / total_responses_per_year) * 100

years <- colnames(non_response_rate)
years <- gsub("X", "", years)

non_response_rate <-as.vector(non_response_rate)
non_response_rate <-unlist(non_response_rate)
non_response_data <- data.frame(years,non_response_rate)

# Plot using ggplot2
ggplot(non_response_data, aes(x = years,y=non_response_rate)) +
  geom_bar(stat = "identity",fill = "skyblue") +
  theme_minimal() +
  labs(title = "Non-Response Rate by Year", x = "Year", y = "Percentage of Non-Responses") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

```

\break

# Discussion

## Labour Market Response Across Economic Crises

## Demographic Disparities in Labour Market Participation

### Younger Workers and Educational Attainment

### Women in the Labour Market

## Political Affiliation and Labour Market Perceptions

##  Ethical Considerations and Bias

## Limitations

## Future Research

## Journal Study: Directions on Non-response Rates

# Conclusion

\appendix

# Appendix {-}

\newpage
# References

### 2024-03-12 scripts/02-data_cleaning.R

@@ -16,7 +16,7 @@ library(here)
 
 #### Clean data ####
 # load dataset that has been cropped for analysis
-data <- read.csv(here::here("/inputs/data/Cropped_Data.csv"))
+data <- read.csv(here::here("inputs/data/Cropped_Data.csv"))
 
 # the first column of the dataset is the names of the rows
 # so we renamed the row names based on first column and 
@@ -41,10 +41,10 @@ rownames(data)[3] <- "Do not Know/Cannot Choose"
 rownames(data)[4] <- "Skipped on Web"
 
 # Save the cleaned data
-write.csv(data, "/inputs/data/Cleaned_Data.csv")
+write.csv(data, "inputs/data/Cleaned_Data.csv")
 
 #Categorize Data============================
-data <- read.csv(here::here("/inputs/data/Cleaned_Data.csv"))
+data <- read.csv(here::here("inputs/data/Cleaned_Data.csv"))
 colnames(data)[1] <- "work_hours"
 colnames(data) <- gsub("X", "", colnames(data))
 
@@ -115,4 +115,4 @@ cate_data <- rbind(No_Response,tweenties,forties,sixties,eighties,more,total)
 cate_data <- data.frame(cbind(Hours,cate_data))
 colnames(cate_data) <- year
 
-write.csv(cate_data,"/inputs/data/cleaned_categorized_data.csv")
+write.csv(cate_data,"inputs/data/cleaned_categorized_data.csv")

### 2024-03-12 scripts/04-test_data.R

@@ -12,7 +12,7 @@
 library(dplyr)
 
 #### Test data ####
-data <- read.csv(here:here("/inputs/data/cleaned_categorized_data.csv"))
+data <- read.csv(here::here("inputs/data/cleaned_categorized_data.csv"))
 test_non_negative <- all(select(data, -work_hours) >= 0)
 print(test_non_negative)
 #The result shows that the year columns does not contain non-negative values.

### 2024-03-12 outputs/paper/paper.qmd
update paper and data

@@
 
-data <- read.csv(here::here("inputs/data/Cleaned_Data.csv"))
+data <- read.csv(here::here("inputs/data/cleaned_data.csv"))
 # Get rid of the first letter X for each of the years
@@
 
+## Survey Introduction
+The supplemental survey is available here: [Google Form Link](https://forms.gle/Ffma5ggEcP6wfumu6)
+
 \newpage

### 2024-03-12 scripts/02-data_cleaning.R

@@ -4,7 +4,7 @@
 # Date: 11 March 2024 
 # Contact: mingjia.chen@mail.utoronto.ca 
 # License: MIT
-# Pre-requisites: R 4.3.2, Cropped_Data.csv
+# Pre-requisites: R 4.3.2, cropped_data.csv
 
 #### Workspace setup ####
 library(janitor)
@@ -16,7 +16,7 @@ library(here)
 
 #### Clean data ####
 # load dataset that has been cropped for analysis
-data <- read.csv(here::here("inputs/data/Cropped_Data.csv"))
+data <- read.csv(here::here("inputs/data/cropped_data.csv"))
 
 # the first column of the dataset is the names of the rows
 # so we renamed the row names based on first column and 
@@ -41,10 +41,10 @@ rownames(data)[3] <- "Do not Know/Cannot Choose"
 rownames(data)[4] <- "Skipped on Web"
 
 # Save the cleaned data
-write.csv(data, "inputs/data/Cleaned_Data.csv")
+write.csv(data, "inputs/data/cleaned_data.csv")
 
 #Categorize Data============================
-data <- read.csv(here::here("inputs/data/Cleaned_Data.csv"))
+data <- read.csv(here::here("inputs/data/cleaned_data.csv"))
 colnames(data)[1] <- "work_hours"
 colnames(data) <- gsub("X", "", colnames(data))
 

### 2024-03-12 scripts/03-data_tabling.R

@@ -4,7 +4,7 @@
 # Date: 11 March 2024 
 # Contact: mingjia.chen@mail.utoronto.ca 
 # License: MIT
-# Pre-requisites: R 4.3.2, Cropped_Data.csv, cleaned_categorized_data.csv
+# Pre-requisites: R 4.3.2, cleaned_Data.csv, cleaned_categorized_data.csv
 
 #download the packages if necessary, then load the packages
 if (!require("pacman")) install.packages("pacman")
@@ -69,7 +69,7 @@ ggplot(data, aes(x = "", y = X2021, fill = work_hours)) +
   theme(plot.title = element_text(hjust = 0.5, size = 16))
 
 # Average Working Hours Comparison between Financial Events
-data <- read.csv(here:here("inputs/data/Cleaned_Data.csv"))
+data <- read.csv(here:here("inputs/data/cleaned_data.csv"))
 # Get rid of the first letter X for each of the years
 colnames(data)[1] <- "work_hours"
 colnames(data) <- gsub("X", "", colnames(data))

### 2024-03-12 outputs/paper/paper.qmd
update appendix

@@
 
+Welcome to our survey, which builds on our research analyzing the impact of economic downturns on labour dynamics in the U.S.
+from 1972 to 2022, based on the General Social Survey (GSS).
+The GSS collects information and historical records of respondents' attitudes and experiences.
+Our study has highlighted significant shifts in working hours, particularly during crises such as the 2008 Financial Crisis and the COVID-19 pandemic, affecting various demographic groups differently.
+This survey seeks to deepen our understanding of these impacts and gather more nuanced data on labour force participation across different economic conditions.
+
+Your participation is voluntary and confidential.
+You may skip any question or withdraw at any time.
+Responses are anonymized and will be used solely for research purposes.
+For any inquiries or additional information, please contact us at evan.hao@mail.utoronto.ca, mingjia.chen@mail.utoronto.ca, and/or catherine.punnoose@mail.utoronto.ca.
+
+## Survey Questions
+\begin{itemize}
+        \item Demographic Information:
+            \begin{enumerate}
+                \item What is your age group?
+                \begin{itemize}
+                  \item Under 18
+                  \item 18-24
+                  \item 25-34
+                  \item 35-44
+                  \item 45-54
+                  \item 55-64
+                  \item 65+
+                \end{itemize}
+                \item What is your highest level of education?
+                \begin{itemize}
+                  \item High school graduate
+                  \item Bachelor's degree
+                  \item Graduate or professional degree
+                \end{itemize}
+                \item Please specify your gender:
+                \begin{itemize}
+                  \item Male
+                  \item Female
+                  \item Non-binary
+                  \item Prefer not to say
+                \end{itemize}
+            \end{enumerate}
+        \item Employment Status and Industry:
+              \begin{enumerate}
+                \item What is your current employment status?
+                \begin{itemize}
+                  \item Employed full-time
+                  \item Employed part-time
+                  \item Unemployed
+                  \item Retired
+                  \item Student
+                \end{itemize}
+                \item If employed, what industry do you work in?
+                \begin{itemize}
+                  \item Manufacturing
+                  \item Construction
+                  \item Retail
+                  \item Hospitality
+                  \item Healthcare
+                  \item Education
+                  \item Information Technology
+                  \item Professional Services
+                  \item Other (please specify)
+                \end{itemize}
+            \end{enumerate}
+        \item Impact of Economic Downturns:
+              \begin{enumerate}
+                \item How did the 2008 financial crisis and/or the COVID-19 pandemic affect your working hours? Did your hours:
+                \begin{itemize}
+                  \item Increase
+                  \item Decrease
+                  \item Stay the same
+                  \item Not applicable/I wasn't employed during these times
+                \end{itemize}
+                \item Did you have to switch to remote work during the COVID-19 pandemic?
+                \begin{itemize}
+                  \item Yes
+                  \item No
+                  \item Not applicable
+                \end{itemize}
+              \end{enumerate}
+        \item Responses to Economic Downturns:
+              \begin{enumerate}
+                \item In times of economic downturn, what support measures do you believe are most effective for workers?
+                \begin{itemize}
+                  \item Unemployment benefits
+                  \item Skills retraining programs
+                  \item Direct financial aid
+                  \item Flexible work arrangements
+                  \item Other (please specify)
+                \end{itemize}
+            \end{enumerate}
+\end{itemize}
+
 \newpage

### 2024-03-12 outputs/paper/paper.qmd
update appendix

@@
 ## Survey Introduction
+
 The supplemental survey is available here: [Google Form Link](https://forms.gle/Ffma5ggEcP6wfumu6)
@@
 ## Survey Questions
+
 \begin{itemize}
@@
 
+## Survey Completion Message
+
+Thank you for participating in our survey.
+Your insights are invaluable to our ongoing research into labour market dynamics and the effects of economic downturns on working hours.
+Your contribution helps us identify areas for targeted interventions and policy recommendations to support vulnerable labour market groups.
 \newpage

### 2024-03-12 outputs/paper/paper.qmd
update appendix
update format
update paper-first draft

@@
 date-format: long
-abstract: "First sentence, second sentence, third sentence."
+abstract: "Historically, economic crises have impacted labour market working patterns and employment levels, but are all groups within the labour market suffering from overall similar trends?
+This study uses data from the U.S.
+General Social Survey (GSS) to investigate the impact of major economic downturns on U.S.
+labour force dynamics, focusing specifically on “hours worked last week.” Analyzing changes in working hours reveals significant reductions, particularly affecting younger workers, those with less education, and women.
+These findings are important since they underscore the necessity for targeted interventions to support the most vulnerable groups in the labour market."
 format: pdf
@@
 
-# Data
+Economic downturns from the 1998 Asian Financial Crisis and 2008 Global Financial Crisis to the unprecedented 2020 COVID-19 pandemic, have significantly shaped labour market landscapes, impacting employment patterns and work hours across the United States.
+These pivotal events, each unique in their severity and global reach, provide a crucial backdrop for examining the labour market's resilience and adaptability amidst fluctuating economic conditions.
+Yet, a critical question arises: How uniformly do these economic shifts affect various segments within the labour market, particularly regarding working hours?
+
+To explore this question, this paper focuses on the U.S.
+General Social Survey (GSS) [@GSS] data to concentrate on the "number of hours worked last week" as a primary metric for labour engagement.
+This study is predicated on the hypothesis that economic declines precipitate a decrease in labour engagement, evidenced by reduced work hours, with varying degrees of impact across different labour groups.
+Through a comparative analysis of periods marked by economic crises against times of economic stability, we aim to dissect the labour market's response mechanisms, spotlighting the sectors and demographic groups most susceptible to economic adversities.
+
+By analyzing the comprehensive GSS data, including variables such as gender, age, and career field, we seek to offer a granular understanding of how major economic crises influence work hours, thereby contributing to a broader discourse on labour market adaptability in the face of economic instability.
+
+Initial analysis reveals notable disparities: younger workers, those with less education, and women experience significant reductions in work hours during economic crises.
+This finding highlights the differential impact of economic downturns across demographic groups and signals the urgent need for targeted policy interventions to mitigate these disparities and bolster labour market resilience.
+
+The ensuing sections of this paper will outline the data's nature and scope, detail the analytical process and findings, and discuss these findings' broader implications for labour market dynamics amidst economic crises.
+The conclusion will synthesize the key insights derived from this analysis, and an appended supplementary survey will propose additional inquiries to explore labour market responses to economic downturns further.
+
+# Data {#sec-data}
+
+The paper uses data collected from the US General Social Survey (GSS) from NORIC at the University of Chicago [@gssFAQ].
+From the dataset, this paper focuses on the "number of hours worked last week" variable, from the years 1972 to 2022.
+This longitudinal approach allows us to compare labour dynamics across different economic downturns, including the 1998 Asian Financial Crisis, the 2008 Global Financial Crisis, and the COVID-19 pandemic in 2020.
 
@@
 The data was downloaded and filtered for the selected variables from the selected data variables from GSS[^1].
-The data cleaning was performed based on value definitions as defined in the GSS codebook [@gssCodebook].
+The data cleaning was performed based on value definitions as defined in the GSS codebooks [@gssCodebook].
 One of the variable names `response` is renamed to be more informative [@tbl-use-var].
@@
 
-## Data Limitations
-
 ## Survey Methodology
 
+From 1972 to 2018, the GSS was conducted through face-to-face interviews.
+In-person interviews facilitated a richer data collection environment, where interviewers could clarify ambiguities and probe deeper into responses.
+This mode of data collection was ideal and allowed interviewers to collect richer data.
+However, in response to the COVID-19 Pandemic, from 2020 to 2021, the GSS transitioned to web surveys as the primary method of collecting data.
+The GSS had a target population of English or Spanish speaking adults (18 years or older) living in households in the United States [@gssFAQ].
+The broad criteria allows a wide range of participants to partake in the survey.
+However, individuals who do not meet the target population are considered out of scope for the survey.
+Individuals who are not English or Spanish speaking, with mental and/or physical conditions that prevent them from participating in the survey are considered to be out of scope for the GSS [@gssFAQ].
+Adjustments in the GSS's respondent selection process, including changes to the Kish grid methodology, pose additional challenges by potentially skewing the demographic representation of respondents.
+The shift towards a web-based format might have disproportionately excluded older demographics, traditionally less engaged with online platforms, thereby affecting the survey's representativeness.
+This demographic shift is crucial, as older workers' employment patterns, which often include more stable, long-term positions or distinct challenges like age-related discrimination, are essential in comprehensively understanding labour market dynamics.
+
+Given the paper's emphasis on the number of hours worked specifically in the years 1998, 2008, and 2020, we focus on the methodology of the corresponding years.
+The survey queried participants with the question, "If working, full or part-time: How many hours did you work last week, at all jobs?" and categorized the responses by hours: No Response, 0-20, 21-40, 41-60, 61-80, and 80+.
+Significantly, between 1998 and 2022, the structure of the question has consistently remained the same.
+This consistency in formatting ensures the data's stability, facilitating a high level of consistency for thorough analysis.
+The data collected from 1998, 2008, and 2021 consists of a combination of in-person, telephone, and web surveys.
+
 ### 1998 Survey Methodology
+
+The 1998 GSS used in-person interviews to collect data.
+A total of 2,832 surveys were conducted.
+English speaking individuals aged 18 or over who lived in non-institutional arrangements within the United States were independently drawn for the 1998 sample [@gssCodebook].
+@fig-Survey-1998 shows a visual of the number of hours worked in 1998.
+
 ```{r}
@@
 
+In 2006, the GSS implemented a new design that uses rotating panels instead of replicating cross-sectional design [@gssCodebook].
+This design was used in the 2008 survey where 2,023 interviews were conducted as well as 1,536 reinterviews from respondents of the 2006 GSS [@gssCodebook2022].
+This design uses a four year model from 2006, 2008, and 2010.
+The survey used an independently drawn sample of English and Spanish speaking individuals living in non-institutional arrangements/households in the United States [@gssCodebook2014].
+@fig-Survey-2008 serves as a visual of the number of hours worked in the year 2008.
+
 ```{r}
@@
 
+###  Strengths in the Survey Methodology
+
+The survey's methodology has several strengths.
+From 1972 to 2018, data was gathered through face-to-face interviews, enabling interviewers to capture diverse and comprehensive information, providing a deeper understanding of respondents.
+Another notable strength is the survey's consistency.
+The General Social Survey (GSS) has maintained a uniform approach since 1972, with minimal alterations in questions and data collection methods each year.
+This consistency facilitates clear year-to-year analyses for researchers.
+The survey, traditionally administered through face-to-face interviews, transitioned to web surveys during the COVID-19 Pandemic.
+Relevance is another key strength of the GSS.
+It encompasses a broad spectrum of demographic, behavioural, and attitudinal questions, covering topics such as civil liberties, crime and violence, and psychological well-being among individuals in the United States [@gssCodebook2022].
+With its almost annual frequency, the survey delivers up-to-date and pertinent information across various fields.
+Furthermore, the survey promotes accessibility by being available to the public.
+This means that anyone interested in the survey's results can freely access the data, enhancing transparency and openness in disseminating valuable information.
+
+### Limitations and Weaknesses of Data Collection
+
+Since 1972, the General Social Survey (GSS) has been gathering data primarily through face-to-face interviews, during which participants were interviewed using a structured questionnaire.
+This approach persisted until the onset of the COVID-19 Global Pandemic, which resulted in the suspension of data collection for the year 2020.
+Subsequently, the data collection methodology underwent a transition from in-person interviews to web-based questionnaires.
+This pandemic-induced shift introduced several variables that could potentially impact data quality and comparability.
+This alteration raises concerns and stands as a notable limitation on the accuracy of reported work hours and the perceived effects of economic crises.
+The move from traditional in-person interviews to web-based surveys brings uncertainties, as the absence of interactive guidance may lead to misinterpretations or superficial engagement with survey questions.
+An essential drawback in the dataset is the limited number of questions asked.
+Only a single survey question was asked, focusing only on obtaining numerical data regarding the respondent's worked hours.
+This weakness limits the understanding of the respondent's demographic details, posing a challenge in the analysis process.
+
 ### Gap in 2020 Data
+
+Due to the COVID-19 Global Pandemic, the GSS Cross-section changed its method of collecting data from in-person interviews to web self-administered questionnaires.
+The purpose of this change was to ensure the safety of respondents and interviewers [@gssCodebook2022].
+The absence of discrete data for 2020 represents a significant analytical challenge, particularly as this year was pivotal in understanding the labour market's immediate reaction to the pandemic's onset.
+The gap prevents a seamless analysis of the transition from pre-pandemic employment conditions to the upheavals initiated by COVID-19, such as mass layoffs and the rapid shift towards remote work.
+This omission obscures our view of the labour market's initial resilience and the effectiveness of the recovery efforts that followed, especially in sectors like hospitality and retail, which experienced direct and severe impacts from lockdown measures.
+To bridge the gap, this paper uses data collected in the 2021 GSS.
+@fig-Survey-2021 shows a visual of the number of hours worked in 2021.
+
 ```{r}
@@
 
+To balance non-responses in the survey, the GSS subsampled non-respondents.
+The fundamental idea of subsampling involves taking a subset of nonrespondents and modifying the weights to maintain an unbiased design [@gssCodebook2014].
+This selected subsample is then scaled up to accurately represent all nonrespondents up to the specified cutoff date.
+By concentrating efforts on a more manageable subset of challenging cases for additional attempts, subsampling has the potential to minimize both response error and nonresponse bias [@gssCodebook2014].
+The GSS's approach to managing non-responses underwent changes, notably in its recent iterations – specifically during the COVID-19 Pandemic.
+As web surveys were used in the 2021 survey, modifications were made to balance non-responses.
+Historically, the survey employed subsampling techniques to mitigate the impact of non-responses, ensuring a representative dataset.
+However, with the introduction of web-based surveys, new categories like "Skipped on Web" were introduced to categorize non-responses.
+This change raises questions about the comparability of data across years and the potential for increased non-response rates.
+Non-responses can significantly affect the analysis of labour market trends, particularly in capturing the full extent of unemployment or underemployment during economic downturns.
+The handling of these non-responses requires scrutiny to assess how it might influence findings on work hours and job stability across different demographic groups and economic sectors.
+
 # Results
@@
 ## Working Hour Comparison Between Financial Events
+
+To more accurately depict the ramifications of economic crises, our study employed data from years closely following significant downturns, specifically comparing 2010 and 2021 to assess the aftermath of the 2008 financial crisis and the COVID-19 pandemic, respectively.
+Due to the absence of data for 2009 in the General Social Survey (GSS), these subsequent years served as our focal points for analysis.
+Our findings, when juxtaposed with data from a year of economic stability, 2018, reveal a notable decrease in working hours for both 2010 and 2021.
+
+This trend in @fig-ave-hour-comparison underscores the tangible impact of economic crises on labour force engagement, highlighting that such downturns invariably lead to reductions in working hours.
+This evidence corroborates the premise that economic crises significantly influence the dynamics of work hours and affirms us the necessity of understanding and mitigating these effects to foster a resilient labour market.
 
@@
 \break
+
+The number of reports in different working hours between the years where the significant events happened were studied in @fig-cate-comparisons.
+According to the histograms, it is interesting that, although they have different numbers, the histograms of the categorized data from the years 1998, 2008, and 2021, and the total years recorded all fit in a similar trend.
+About half of the participants did not respond to the question.
+Aside from those who did not respond to the question, most of the participants worked between 40-60 hours and some worked between 21-40.
+Participants rarely worked over 80 hours.
+This could mean that even after suffering from significant historical events that negatively impact economics, the trend of working hours stays relatively similar to the general trend for data from 1997 to 2022.
+This finding does not mean that the numbers of reports for each working hour were the same: more participants responded to the question in the years 1998 and 2021 compared to the year 2008.
+This could mean that there were more job opportunities in 1998 and 2021 than in 2008.
 
@@
 \break
+
+Non-response rates we illustrated in @fig-nonresponse-rate, in addition, could help indicate a significant difference in participants and data collection between the years.
+The year 1972, for example, is evidence of the gap in the data set; even though it is included in the data set, the non-response rate is 100%, meaning that no answers to this question were collected during that year.
+The non-response rate in general is similar among the years, not indicating significant differences between the years even during the financial crisis.
 
@@
 
+We find that a downward trend in the economy leads to a similar decline in labour force hours and hours worked, although the impact is felt differently across industries and demographic groups; this emphasizes the multifaceted nature of the labour market and economic pressures.
+
 ## Labour Market Response Across Economic Crises
 
-## Demographic Disparities in Labour Market Participation
+GSS Data [^1] provides hours worked before and after a severe recession to reveal the trend of fewer hours worked during periods of economic instability, as @fig-ave-hour-comparison shows.
+The research perspective of @Wang_Madsen_Steiner_2016 shows that during the 2008 financial crisis, working hours in industries such as manufacturing and construction decreased significantly, mainly due to their direct link to the economic cycle.
+These industries tend to respond quickly to economic downturns because of their reliance on consumer demand and investment, which typically decline during financial crises.
+The above reflects the direct impact of the economic cycle on directly related industries, resulting in reduced working hours.
+In contrast, working hours in health care and education are more stable.
+These industries are somewhat insulated from an immediate economic downturn because demand for their services remains consistent regardless of the economic environment.
+Especially during times of crisis such as a pandemic, the need for healthcare may even increase.
 
-### Younger Workers and Educational Attainment
+The COVID-19 pandemic has brought new disruptions to the labour market, with an unprecedented shift to remote work and flexible work arrangements.
+By analyzing GSS data and @fig-ave-hour-comparison shows that 2021, a pandemic year, has experienced a more serious decline in working hours than in 1998 and 2008.
+The research of
+@Chen_Yeh_2021 explains that this is because sectors that have traditionally been limited to physical presence, such as retail and hospitality, have faced even more significant challenges during COVID compared with historical economic crises, which have led to more substantial job losses and reduced hours.
+In contrast, sectors that have been able to transition to remote operations, such as information technology and professional services, have seen less impact on working hours, highlighting the changing nature of work in response to external shocks.
 
-### Women in the Labour Market
+## COVID-19’s Sharply Reduced Working Hours and Women in the Labour Market
 
-## Political Affiliation and Labour Market Perceptions
+The insights from @Chen_Yeh_2021 can further help us analyze the reasons for the substantial decrease in working hours in 2021.
+@Chen_Yeh_2021 believe women face unique challenges during the COVID-19 pandemic, not only because they are overrepresented in industries such as hospitality and retail, which have been severely affected by lockdowns and restrictions, but also Because of increased caring responsibilities.
+@Singh_Shirazi_Turetken_2022 suggests that women have to cope with the dual pressures of work and family responsibilities more than their male counterparts.
+School closures and the need for childcare have placed additional burdens on women, with significant impacts on their working hours and labour force participation.
 
@@
 
+We believe that ethical considerations and minimizing bias are cornerstones of responsible research, particularly when delving into labour market responses to economic downturns.
+Our approach to ethics and bias therefore emphasizes informed consent, privacy and data protection.
+
+We agree that strong measures should be in place to ensure participant confidentiality and data protection, as mentioned in the GSS codebook [@gssCodebook].
+This involves using a secure database to store sensitive information and encrypting participant details to prevent unauthorized access.
+
+In addition, we adopted several strategies to address potential bias in our research.
+Recognizing the risk of sampling bias, whereby certain groups may be over-represented, we have diversified our outreach methods.
+Inspired by the GSS codebook [@gssCodebook], we recommend that new survey approaches post-2020 could reach participants through a variety of channels, including social media, community communications, and local organizations to ensure a broad range of demographics.
+
 ## Limitations
+
+Our analysis grounded in the rich dataset provided by the General Social Survey (GSS) [^1], navigates through a complex terrain of labour market dynamics in the wake of economic crises.
+However, as mentioned in the data @sec-data, several limitations inherent to the dataset and the broader research approach necessitate a cautious interpretation of our findings.
+
+The original data only provides simple data on working hours, but in @gssCodebook, GSS has a detailed explanation of the data survey method, such as interviewing random people through questionnaires.
+The sensitive nature of questions related to economic hardships and employment challenges may lead to a degree of response bias.
+Despite advancements in survey techniques since the 1970s, the discomfort associated with disclosing personal economic impacts or job losses can limit the diversity and authenticity of responses collected.
+Framing questions within the GSS regarding employment and economic resilience may also inadvertently reflect biases or presuppositions.
+This phenomenon could mirror previous findings where respondents mask their true beliefs on topics, potentially skewing the data towards more socially acceptable responses.
+
+Further analysis [@gssCodebook], the ambiguity of survey question phrasing and response options poses another challenge.
+Economic crises and their effects are multifaceted, with nuances that single-answer survey questions might not fully capture.
+The lack of open-ended questions or opportunities for respondents to elaborate on their experiences restricts our understanding of the depth and breadth of economic downturns' impacts on individual work patterns and perceptions.
+
+In addition to the above, the evolving nature of the labour market, marked by the rise of gig work, remote employment, and the digital economy, poses significant challenges to capturing the full spectrum of employment experiences during economic downturns.
+These changes underscore the need for survey methodologies to adapt and evolve, ensuring that emerging forms of work and employment are adequately represented in the data.
+
+While it is fitting that necessary updates to survey methods, the change in GSS's methodology [^1], including sampling techniques and data collection strategies, can introduce inconsistencies in longitudinal data, complicating efforts to draw definitive conclusions about trends over time.
+For example, in 2020, due to COVID-19, most of the data were suspended and a small part was combined with online surveys, making it controversial to put it together with the previous year's data recorded according to normal procedures.
+
+The demographic representation within the GSS data warrants careful consideration.
+Variations in sample composition by gender, age, education level, and other demographic factors can influence the generalizability of our findings.
+We worry that the potential for overrepresentation or underrepresentation of certain groups underscores the importance of employing robust analytical techniques to account for these disparities and interpret the data within the context of its limitations.
+
+Finally, our paper also has certain limitations in processing data as shown in data @sec-data.
+One limitation stems from our decision to analyze the years immediately following the economic crisis (2010 and 2021) rather than the year immediately following the recession itself.
+This choice was made partly because of the lack of data for 2009 in the General Social Survey (GSS), necessitating the need to use 2010 (the second year of the economic crisis) as a proxy to measure the post-crisis impact of the 2008 financial recession.
+Likewise, given the unprecedented impact of the COVID-19 pandemic in 2020, the selection of 2021 was intended to capture its consequences rather than 2022, which could be compared to the 2010 selection.
+
+This methodological decision, while practical, introduces a temporal shift that may not fully capture the direct impact of the economic crisis on working hours.
+The absence of 2009 GSS data leaves a significant gap in our longitudinal analysis because it limits our ability to directly compare the pre-crisis, crisis, and post-crisis periods consistently.
+
+## Journal Study: Directions on Non-response Rates
+
+In addressing non-response rates within labour market surveys, @Groves_Peytcheva_2008 provides some suggestions for directions for our consideration.
+They advocate for tailored communication and mixed-mode survey approaches as effective measures against non-response bias (Journal of Official Statistics, 24(2), 167-189).
+For instance, future research could look into the success of the Health and Retirement Study, which employs a mixed-mode design, combining in-person interviews with telephone and online follow-ups to accommodate participant preferences and improve response rates.
+These examples underscore the potential of adopting innovative methodologies and technologies in labour market surveys to ensure more representative data.
 
@@
 
-## Journal Study: Directions on Non-response Rates
+Based on the insights and limitations discussed previously, we propose some potential future research directions to address these challenges.
+
+To tackle response bias, a common hurdle in surveys on sensitive topics like economic impact, future efforts could lean more heavily into techniques that safeguard participant anonymity and confidentiality.
+For example, the Pew Research Center's [@Pew_Research_Center_2021] method of ensuring anonymity in their political opinion polls could serve as a model, enhancing respondent confidence and honesty.
+Briefly, their approach is characterized by random sampling to select representativeness.
+The main thing is that they will demonstrate to the public how the respondent's data is protected through encryption and strict privacy protocols, ensuring that no personally identifiable information is recorded or stored.
+
+Survey design also requires attention to minimize ambiguity and enhance response quality.
+Future surveys could take a leaf from the book of market research, where detailed response options and open-ended questions are standard.
+This would help capture the full spectrum of employment experiences during crises.
+Pre-testing questions, a strategy often employed by the Census Bureau, could ensure questions are understood as intended, improving the quality of data collected.
+
+In addition, addressing demographic disparities calls for a focused examination of how different identities intersect to impact labour market experiences.
+Drawing inspiration from studies like the Health and Retirement Study, which investigates how socio-demographic factors affect retirement planning, future research could explore how race, gender, age, and education level intertwine to influence employment patterns during economic challenges.
+
+For future labour market survey research, we refer to the method proposed by Groves and Peytcheva [@Groves_Peytcheva_2008] above to eliminate non-response rates and bias as much as possible.
+We recommend a hybrid offline and online survey design; this approach can improve participation rates and data representativeness by accommodating a wider range of respondent preferences and accessibility.
+For example, incorporating new technologies such as mobile survey apps or secure online platforms could reduce participation barriers.
+
+Regarding the limitations of our data processing methods, an essential way to solve the above limitations for future research is to use more diverse data sources and methodologies.
+We should consider utilizing or fusing other databases to fill in the gap years in the GSS data, such as 2009, to more fully capture the direct impact of the economic crisis and its immediate response to the labour market.
+
+By combining these targeted strategies with examples of existing research practice, we believe that future research can more effectively capture labour market outcomes related to hours worked and the economy.
 
 # Conclusion
+
+In summary, we used U.S.
+General Social Survey (GSS) data [^1] to study the impact of economic recessions on labour force dynamics from 1972 to 2022, trying to prove that economic downturns lead to a decline in average working hours.
+Our findings show that hours worked did fall during different recessions, notably the 1998 Asian Financial Crisis, the 2008 Financial Crisis and the COVID-19 pandemic in 2020, with the 2021 data showing the steepest decline.
+By analyzing studies in other academic journals, including @Wang_Madsen_Steiner_2016, @Chen_Yeh_2021, @Groves_Peytcheva_2008, @Pew_Research_Center_2021, and @Singh_Shirazi_Turetken_2022, we believe that potential Reasons for this include the varying degrees of dependence of industries on the economic cycle and the increase in various social issues, such as the uneven impact on different industries and the fact that women have been disproportionately hit harder by family during COVID.
+
+However, during the analysis process, we also found that there are some limitations in the GSS study, such as changes in data collection methods and the processing of non-response rates.
+Future research could explore how to overcome these limitations by addressing factors such as response bias and balancing demographic differences.
+While our study poses challenges, we cannot allow progress in labour market equality and adaptability to take decades more to achieve.
+Future research should focus on exploring effective policies to support the groups most vulnerable to economic hardship and ensure that working hours in the labour market are not too severely affected.
 
@@
 
-\begin{itemize}
-        \item Demographic Information:
 \begin{enumerate}
@@
     \end{itemize}
-            \end{enumerate}
-        \item Employment Status and Industry:
-              \begin{enumerate}
     \item What is your current employment status?
@@
     \end{itemize}
-            \end{enumerate}
-        \item Impact of Economic Downturns:
-              \begin{enumerate}
     \item How did the 2008 financial crisis and/or the COVID-19 pandemic affect your working hours? Did your hours:
@@
     \end{itemize}
-              \end{enumerate}
-        \item Responses to Economic Downturns:
-              \begin{enumerate}
     \item In times of economic downturn, what support measures do you believe are most effective for workers?
@@
 \end{enumerate}
-\end{itemize}
 
@@
 Your contribution helps us identify areas for targeted interventions and policy recommendations to support vulnerable labour market groups.
+
 \newpage
+
 # References

### 2024-03-14 scripts/00-simulate_data.R
modified simulate scripts

@@ -1,35 +1,29 @@
-#### Preamble ####
-# Purpose:  Simulate the dataset for code testing
-# Author: Mingjia Chen, Catherine Punnoose, Tianen (Evan) Hao
-# Date: 11 March 2024 
-# Contact: mingjia.chen@mail.utoronto.ca 
-# License: MIT
-# Pre-requisites: none
-
-#### Workspace setup ####
 library(tibble)
 library(dplyr)
+library(tidyr)
 
-
-#### Simulate data ####
 # Define years and work hours categories
-years <- c(1972, 1973, 1974, 1975, 1976, 1977, 1978, 1980, 1981, 1982, 1983, 1984, 1985, 1986, 1987, 1988, 1989, 1990, 1991, 1992, 1993, 1994, 1995, 1996, 1997, 1998, 1999, 2000, 2001, 2002, 2003, 2004, 2005, 2006, 2008, 2010, 2012, 2014, 2016, 2018, 2021, 2022)
+years <- c(1972, 1973, 1974, 1975, 1976, 1977, 1978, 1980, 1981, 1982, 
+           1983, 1984, 1985, 1986, 1987, 1988, 1989, 1990, 1991, 1992, 
+           1993, 1994, 1995, 1996, 1997, 1998, 1999, 2000, 2001, 2002, 
+           2003, 2004, 2005, 2006, 2008, 2010, 2012, 2014, 2016, 2018, 
+           2021, 2022)
 work_hours_categories <- c("No Response", "0-20", "21-40", "41-60", "61-80")
 
-# Create the initial tibble with work_hours column
-simulated_data <- tibble(work_hours = work_hours_categories)
-
-# Add each year as a new column with simulated data
+# Simulate data
 set.seed(123) # For reproducibility
-for(year in years) {
-  simulated_data[[as.character(year)]] <- runif(n = length(work_hours_categories), min = 50, max = 2000)
-}
+simulated_data <- tibble(year = rep(years, each = length(work_hours_categories)),
+                         work_hours = rep(work_hours_categories, times = length(years)),
+                         value = runif(n = length(years) * length(work_hours_categories), min = 50, max = 2000))
 
-# Correct test for a specific year's range of values using appropriate column referencing
-test_year_range <- all(simulated_data[["2022"]] >= 50 & simulated_data[["2022"]] <= 2000)
+# Pivot to wide format
+simulated_data_wide <- simulated_data %>%
+  pivot_wider(names_from = year, values_from = value)
[…]

### 2024-03-14 outputs/paper/paper.qmd
update paper

@@
 ---
-title: "Labour Market Resilience"
-subtitle: "Economic Crisis Has Diverse Impacts on Industry Work Hours"
+title: "U.S. Labour Market Resilience"
+subtitle: "Impact Analysis of Economic Crises on Industry Work Hours in 1998, 2008 and 2020"
 author: 
@@
 date-format: long
-abstract: "Historically, economic crises have impacted labour market working patterns and employment levels, but are all groups within the labour market suffering from overall similar trends?
-This study uses data from the U.S.
+abstract: "Economic crises have impacted labour market working patterns and employment levels, but are all groups within the labour market suffering from similar trends?
+Focusing on the Asian Financial Crisis, the Global Financial Crisis, and the COVID-19 pandemic, this study uses data from the U.S.
 General Social Survey (GSS) to investigate the impact of major economic downturns on U.S.
-labour force dynamics, focusing specifically on “hours worked last week.” Analyzing changes in working hours reveals significant reductions, particularly affecting younger workers, those with less education, and women.
-These findings are important since they underscore the necessity for targeted interventions to support the most vulnerable groups in the labour market."
+labour force dynamics, focusing specifically on “hours worked last week.” Our analysis reveals that economic downturns lead to a decline in average working hours, and identifies disparities in the effects of economic crises on demographic groups, with women and younger workers disproportionately affected.
+These findings underscore the necessity for targeted interventions to support the most vulnerable groups in the labour market."
 format: pdf
@@
 
-# Introduction
+# Introduction {#sec-intro}
 
-Economic downturns from the 1998 Asian Financial Crisis and 2008 Global Financial Crisis to the unprecedented 2020 COVID-19 pandemic, have significantly shaped labour market landscapes, impacting employment patterns and work hours across the United States.
-These pivotal events, each unique in their severity and global reach, provide a crucial backdrop for examining the labour market's resilience and adaptability amidst fluctuating economic conditions.
-Yet, a critical question arises: How uniformly do these economic shifts affect various segments within the labour market, particularly regarding working hours?
+Economic downturns, from the 1998 Asian Financial Crisis and 2008 Global Financial Crisis to the 2020 COVID-19 pandemic, have significantly impacted the U.S.
+labour market, affecting employment patterns and work hours.
+These events, unique in severity and reach, provide a crucial backdrop for examining labour market resilience and adaptability.
+A critical question arises: How uniformly do these shifts affect labour market segments, especially in work hours?
 
-To explore this question, this paper focuses on the U.S.
-General Social Survey (GSS) [@GSS] data to concentrate on the "number of hours worked last week" as a primary metric for labour engagement.
-This study is predicated on the hypothesis that economic declines precipitate a decrease in labour engagement, evidenced by reduced work hours, with varying degrees of impact across different labour groups.
-Through a comparative analysis of periods marked by economic crises against times of economic stability, we aim to dissect the labour market's response mechanisms, spotlighting the sectors and demographic groups most susceptible to economic adversities.
+This paper uses U.S.
+General Social Survey (GSS) [@GSS] data to examine the "number of hours worked last week" as a key measure of labour engagement.
+We hypothesize that economic downturns lead to decreased labour engagement, seen in reduced work hours, impacting labour groups differently.
+By comparing periods of economic crises with times of stability, we aim to understand the labour market's responses, focusing on the most affected sectors and demographic groups.
 
-By analyzing the comprehensive GSS data, including variables such as gender, age, and career field, we seek to offer a granular understanding of how major economic crises influence work hours, thereby contributing to a broader discourse on labour market adaptability in the face of economic instability.
+Our analysis of GSS data, including gender, age, and career field variables, seeks to provide detailed insights into how economic crises affect work hours, contributing to discussions on labour market flexibility during economic instability.
 
-Initial analysis reveals notable disparities: younger workers, those with less education, and women experience significant reductions in work hours during economic crises.
-This finding highlights the differential impact of economic downturns across demographic groups and signals the urgent need for targeted policy interventions to mitigate these disparities and bolster labour market resilience.
+Initial findings show disparities: younger workers, those with less education, and women face significant work-hour reductions during crises.
+This underscores the need for targeted policy interventions to address these disparities and strengthen labour market resilience.
 
-The ensuing sections of this paper will outline the data's nature and scope, detail the analytical process and findings, and discuss these findings' broader implications for labour market dynamics amidst economic crises.
-The conclusion will synthesize the key insights derived from this analysis, and an appended supplementary survey will propose additional inquiries to explore labour market responses to economic downturns further.
+This paper begins with an [Introduction] framing the impact of economic downturns on work hours.
+It is followed by the [Data] section detailing methodology and cleaning efforts.
+In the [Results], we analyze work hours and nonresponse rates, leading to the [Discussion] on labour market responses to crises, including the impact of COVID-19, and addressing ethical issues.
+We later acknowledge our paper's Limitations, suggest paths for Future Research, especially on enhancing response rates, and conclude with a synthesis of our insights.
+The [Appendix] provides further survey information.
 
@@
 ## Source Data
+
+From the dataset, we used the variable “response” to collect the respondent’s responses.
+For clarity, the variable was renamed to “work hours” as the respondent’s response was the number of hours they worked.
+Another variable used is “year”.
+The purpose of this variable is to collect the year the survey was conducted.
 
@@
 
-ggplot(data, aes(x = "", y = X1998, fill = work_hours)) +
-  geom_bar(stat = "identity", width = 1) +
-  coord_polar("y", start = 0) +
-  scale_fill_brewer(palette = "Set3") +  # Use a color palette
-  theme_void() +  # Remove background and gridlines
-  labs(title = "1998 Survey Results") +
-  theme(plot.title = element_text(hjust = 0.5, size = 16))
 ```
@@
 
-ggplot(data, aes(x = "", y = X2008, fill = work_hours)) +
-  geom_bar(stat = "identity", width = 1) +
-  coord_polar("y", start = 0) +
-  scale_fill_brewer(palette = "Set3") +  # Use a color palette
-  theme_void() +  # Remove background and gridlines
-  labs(title = "2008 Survey Results") +
-  theme(plot.title = element_text(hjust = 0.5, size = 16))
 ```
@@
 
-ggplot(data, aes(x = "", y = X2021, fill = work_hours)) +
-  geom_bar(stat = "identity", width = 1) +
-  coord_polar("y", start = 0) +
-  scale_fill_brewer(palette = "Set3") +  # Use a color palette
-  theme_void() +  # Remove background and gridlines
-  labs(title = "2021 Survey Results") +
-  theme(plot.title = element_text(hjust = 0.5, size = 16))
 ```
@@
 
-# Results
+# Results {#sec-results}
 
@@
 
-# Discussion
+# Discussion {#sec-discussion}
 
@@
 School closures and the need for childcare have placed additional burdens on women, with significant impacts on their working hours and labour force participation.
+
+##  Policy Interventions: Short-Term Relief and Long-Term Resilience
+
+The significant drop in work hours during economic downturns underscores the importance of policy interventions and social welfare to support both immediate recovery and long-term labour market resilience.
+For example, during the COVID-19 pandemic, expanded unemployment benefits and direct financial aid provided critical support demonstrating effective short-term relief strategies, as @MacKinnon mentioned in his article.
+
+Furthermore, long-term measures, such as retraining programs for emerging sectors, emphasize the need for policies that bolster workforce adaptability.
+By equipping workers with new skills, these programs facilitate transitions to stable employment in growing industries.
+For the gig economy, particularly impacted by economic crises, requires policies ensuring social security benefits and income stability.
+Implementing health and safety standards for gig workers can also enhance their job security and well-being.
 
@@
 
-# Conclusion
+# Conclusion {#sec-conclusion}
 

### 2024-03-14 outputs/paper/paper.qmd
update graphs

@@
 English speaking individuals aged 18 or over who lived in non-institutional arrangements within the United States were independently drawn for the 1998 sample [@gssCodebook].
-@fig-Survey-1998 shows a visual of the number of hours worked in 1998.
-
-```{r}
-#| label: fig-Survey-1998
-#| tbl-cap: Overview of the 1998 Survey Data 
-#| echo: false
-#| warning: false
-#| message: false
-data <- read.csv(here::here("inputs/data/cleaned_categorized_data.csv"))
-data <- data[1:6,]
-
-```
-\break
+@fig-cate-comparisons shows a visual of the number of hours worked in 1998.
 
@@
 The survey used an independently drawn sample of English and Spanish speaking individuals living in non-institutional arrangements/households in the United States [@gssCodebook2014].
-@fig-Survey-2008 serves as a visual of the number of hours worked in the year 2008.
-
-```{r}
-#| label: fig-Survey-2008
-#| tbl-cap: Overview of the 2008 Survey Data 
-#| echo: false
-#| warning: false
-#| message: false
-
-data <-read.csv(here::here("inputs/data/cleaned_categorized_data.csv"))
-data <- data[1:6,]
-
-```
-\break
+@fig-cate-comparisons serves as a visual of the number of hours worked in the year 2008.
 
@@
 To bridge the gap, this paper uses data collected in the 2021 GSS.
-@fig-Survey-2021 shows a visual of the number of hours worked in 2021.
+@fig-cate-comparisons shows a visual of the number of hours worked in 2021.
 
 ```{r}
-#| label: fig-Survey-2021
-#| tbl-cap: Overview of the 2021 Survey Data 
+#| label: fig-cate-comparisons
+#| fig-cap: Categorical Working Hour Comparison between the Years
+#| fig-subcap: ["Asian Financial Crisis (1998)","World Financial Crisis(2008)","During Covid-19 Pandemic (2021)", "Total"]
+#| layout-ncol: 2
 #| echo: false
@@
 #| message: false
+
+#still need to modify the graphs
+
 data <- read.csv(here::here("inputs/data/cleaned_categorized_data.csv"))
-data <- data[1:6,]
+data <- data[c(2:ncol(data))]
+# Get rid of the first letter X for each of the years
+colnames(data) <- gsub("X", "", colnames(data))
 
+Data_1998 <- select(data,work_hours,`1998`)
+ggplot(Data_1998,aes(x=work_hours,y=`1998`)) +
+  geom_bar(stat="identity") + 
+  theme_minimal() + # Make the theme neater
+  labs(x = "Hours of Working", y = "Number of Reports") +
+  scale_color_brewer(palette = "Set1") +
+  theme(legend.position = "bottom")
+
+Data_2008 <- select(data,work_hours,`2008`)
+ggplot(Data_2008,aes(x=work_hours,y=`2008`)) +
+  geom_bar(stat="identity") + 
+  theme_minimal() + # Make the theme neater
+  labs(x = "Hours of Working", y = "Number of Reports") +
+  scale_color_brewer(palette = "Set1") +
+  theme(legend.position = "bottom")
+
+Data_2021 <- select(data,work_hours,`2021`)
+ggplot(Data_2021,aes(x=work_hours,y=`2021`)) +
+  geom_bar(stat="identity") + 
+  theme_minimal() + # Make the theme neater
+  labs(x = "Hours of Working", y = "Number of Reports") +
+  scale_color_brewer(palette = "Set1") +
+  theme(legend.position = "bottom")
+
+Data_Total <- select(data,work_hours,Total)
+ggplot(Data_Total,aes(x=work_hours,y= Total)) +
+  geom_bar(stat="identity") + 
+  theme_minimal() + # Make the theme neater
+  labs(x = "Hours of Working", y = "Number of Reports") +
+  scale_color_brewer(palette = "Set1") +
+  theme(legend.position = "bottom")
 ```
+
+\break
 
@@
 This could mean that there were more job opportunities in 1998 and 2021 than in 2008.
-
-```{r}
-#| label: fig-cate-comparisons
-#| fig-cap: Categorical Working Hour Comparison between the Years
-#| fig-subcap: ["Asian Financial Crisis (1998)","World Financial Crisis(2008)","During Covid-19 Pandemic (2021)", "Total"]
-#| layout-ncol: 2
-#| echo: false
-#| warning: false
-#| message: false
-
-#still need to modify the graphs
-
-data <- read.csv(here::here("inputs/data/cleaned_categorized_data.csv"))
-data <- data[c(2:ncol(data))]
-# Get rid of the first letter X for each of the years
-colnames(data) <- gsub("X", "", colnames(data))
-
-Data_1998 <- select(data,work_hours,`1998`)
-ggplot(Data_1998,aes(x=work_hours,y=`1998`)) +
-  geom_bar(stat="identity") + 
-  theme_minimal() + # Make the theme neater
-  labs(x = "Working Hours", y = "Number of Reports") +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom")
-
-Data_2008 <- select(data,work_hours,`2008`)
-ggplot(Data_2008,aes(x=work_hours,y=`2008`)) +
-  geom_bar(stat="identity") + 
-  theme_minimal() + # Make the theme neater
-  labs(x = "Working Hours", y = "Number of Reports") +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom")
-
-Data_2021 <- select(data,work_hours,`2021`)
-ggplot(Data_2021,aes(x=work_hours,y=`2021`)) +
-  geom_bar(stat="identity") + 
-  theme_minimal() + # Make the theme neater
-  labs(x = "Working Hours", y = "Number of Reports") +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom")
-
-Data_Total <- select(data,work_hours,Total)
-ggplot(Data_Total,aes(x=work_hours,y= Total)) +
-  geom_bar(stat="identity") + 
-  theme_minimal() + # Make the theme neater
-  labs(x = "Working Hours", y = "Number of Reports") +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom")
-```
 

### 2024-03-14 scripts/02-data_cleaning.R
update cleaning script

@@ -35,25 +35,22 @@ colnames(data) <- gsub("X", "", colnames(data))
 # Rename part of the row names 
 #(i.e. change .i Inapplicable into Inapplicable for better
 #data representation) 
-rownames(data)[1] <- "Inapplicable"
-rownames(data)[2] <- "No answer"
-rownames(data)[3] <- "Do not Know/Cannot Choose"
-rownames(data)[4] <- "Skipped on Web"
+rownames(data)[1:4] <- c("Inapplicable","No answer","Do not Know/Cannot Choose","Skipped on Web")
 
 # Save the cleaned data
 write.csv(data, "inputs/data/cleaned_data.csv")
 
-#Categorize Data============================
-data <- read.csv(here::here("inputs/data/cleaned_data.csv"))
+#### Categorize Data #####
 colnames(data)[1] <- "work_hours"
 colnames(data) <- gsub("X", "", colnames(data))
-
 cate_data <- data
+
 year <- colnames(data)
 Hours <- c("No Response","0-20","21-40","41-60","61-80","80+","Total")
 
 col_number <- ncol(cate_data) -1
 
+#summarize all the responses in one category
 filtered_df1 <- cate_data %>%
   filter(work_hours < 20) 
 
@@ -107,10 +104,12 @@ for(i in 1:col_number){
   No_Response[i] <- sum(filtered_df6[, i+1])
 }
 
+#remove unwanted dataframes
 rm(filtered_df1,filtered_df2,filtered_df3,filtered_df4,filtered_df5,filtered_df6)
 
-total <- data[95,2:36]
+total <- data[95,2:35]
 
+#combine all the data
 cate_data <- rbind(No_Response,tweenties,forties,sixties,eighties,more,total)
 cate_data <- data.frame(cbind(Hours,cate_data))
 colnames(cate_data) <- year

### 2024-03-14 paper/paper.qmd
update file name consistency and folder structure

--- 2024-03-14 outputs/paper/paper.qmd
@@
 However, with the introduction of web-based surveys, new categories like "Skipped on Web" were introduced to categorize non-responses.
-This change raises questions about the comparability of data across years and the potential for increased non-response rates.
+This change raises questions about the comparability of data across years and the potential for increased non-response rates (@fig-nonresponse-rate).
 Non-responses can significantly affect the analysis of labour market trends, particularly in capturing the full extent of unemployment or underemployment during economic downturns.
@@
 
+```{r}
+#| label: fig-nonresponse-rate
+#| fig-cap: Nonresponse Rates
+#| echo: false
+#| warning: false
+#| message: false
+
+# Calculate percentages
+data <- read.csv(here::here("inputs/data/cleaned_categorized_data.csv"))
+data <- data[c(2:ncol(data))]
+data <- data[1:6,]
+
+#colnames(data) <- paste(colnames(data),"Year",sep="_")
+
+colnames(data)<- as.character(colnames(data))
+
+#data_long <- data %>% 
+#  pivot_longer(cols = everything(), names_to = "WorkHours", values_to #= "Response")
+
+# Select the 'No Response' row and remove the first column which is not needed for the plot
+no_response_data <- data[data$work_hours == 'No Response', -1]
+
+# We also need to remove the 'Total' column as we did in the Python example
+no_response_data <- no_response_data[-length(no_response_data)]
+
+# Calculate total responses per year excluding the 'work_hours' and 'Total' columns
+
+data <- read.csv(here::here("inputs/data/cleaned_categorized_data.csv"))
+data <- data[c(3:ncol(data))]
+
+total_responses_per_year <- as.vector(data[7,])
+total_responses_per_year <- unlist(total_responses_per_year)
+
+# Calculate non-response rate as a percentage
+non_response_rate <- (no_response_data / total_responses_per_year) * 100
+
+years <- colnames(non_response_rate)
+years <- gsub("X", "", years)
+
+non_response_rate <-as.vector(non_response_rate)
+non_response_rate <-unlist(non_response_rate)
+non_response_data <- data.frame(years,non_response_rate)
+
+# Plot using ggplot2
+ggplot(non_response_data, aes(x = years,y=non_response_rate)) +
+  geom_bar(stat = "identity",fill = "skyblue") +
+  theme_minimal() +
+  labs(title = "Non-Response Rate by Year", x = "Year", y = "Percentage of Non-Responses") +
+  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
+
+```
+
+\break
+
 # Results {#sec-results}
 
-## Working Hour Comparison Between Financial Events
+## Average Working Hour Comparison Between Financial Events
 
@@
 
+## Nonreponse Rate
+
 Non-response rates we illustrated in @fig-nonresponse-rate, in addition, could help indicate a significant difference in participants and data collection between the years.
@@
 The non-response rate in general is similar among the years, not indicating significant differences between the years even during the financial crisis.
-
-## Nonreponse Rate
-```{r}
-#| label: fig-nonresponse-rate
-#| fig-cap: Nonresponse Rates
-#| echo: false
-#| warning: false
-#| message: false
-
-# Calculate percentages
-data <- read.csv(here::here("inputs/data/cleaned_categorized_data.csv"))
-data <- data[c(2:ncol(data))]
-data <- data[1:6,]
-
-#colnames(data) <- paste(colnames(data),"Year",sep="_")
-
-colnames(data)<- as.character(colnames(data))
-
-#data_long <- data %>% 
-#  pivot_longer(cols = everything(), names_to = "WorkHours", values_to #= "Response")
-
-# Select the 'No Response' row and remove the first column which is not needed for the plot
-no_response_data <- data[data$work_hours == 'No Response', -1]
-
-# We also need to remove the 'Total' column as we did in the Python example
-no_response_data <- no_response_data[-length(no_response_data)]
-
-# Calculate total responses per year excluding the 'work_hours' and 'Total' columns
-
-data <- read.csv(here::here("inputs/data/cleaned_categorized_data.csv"))
-data <- data[c(3:ncol(data))]
-
-total_responses_per_year <- as.vector(data[7,])
-total_responses_per_year <- unlist(total_responses_per_year)
-
-# Calculate non-response rate as a percentage
-non_response_rate <- (no_response_data / total_responses_per_year) * 100
-
-years <- colnames(non_response_rate)
-years <- gsub("X", "", years)
-
-non_response_rate <-as.vector(non_response_rate)
-non_response_rate <-unlist(non_response_rate)
-non_response_data <- data.frame(years,non_response_rate)
-
-# Plot using ggplot2
-ggplot(non_response_data, aes(x = years,y=non_response_rate)) +
-  geom_bar(stat = "identity",fill = "skyblue") +
-  theme_minimal() +
-  labs(title = "Non-Response Rate by Year", x = "Year", y = "Percentage of Non-Responses") +
-  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
-
-```
-
-\break
 
@@
 
-# Appendix {-}
+# Appendix
 

### 2024-03-14 paper/paper.qmd
Update according to feedbacks

@@
 title: "U.S. Labour Market Resilience"
-subtitle: "Impact Analysis of Economic Crises on Industry Work Hours in 1998, 2008 and 2020"
+subtitle: "Analysis of Economic Crises on Industry Work Hours in 1998, 2008 and 2020 US General Social Surveys"
 author: 
@@
 
-The paper uses data collected from the US General Social Survey (GSS) from NORIC at the University of Chicago [@gssFAQ].
+The paper uses data collected from the US General Social Survey (GSS) from NORIC at the University of Chicago [@GSS].
 From the dataset, this paper focuses on the "number of hours worked last week" variable, from the years 1972 to 2022.
@@
 The data cleaning was performed based on value definitions as defined in the GSS codebooks [@gssCodebook].
-One of the variable names `response` is renamed to be more informative [@tbl-use-var].
+One of the variable names `response` is renamed to be more informative (@tbl-use-var).
 
-The data was thus been cleaned by using the open source statistically programming language R [@citeR], with libraries `tidyverse` [@tidyverse], `ggplot2` [@ggplot2], `dplyr` [@dplyr], `readr` [@readr], `tibble` [@tibble], `here` [@here], `kableExtra` [@kableExtra], `janitor` [@janitor], and `knitr` [@knitr].
+The data was cleaned by using the open source statistically programming language R [@citeR], with libraries `tidyverse` [@tidyverse], `ggplot2` [@ggplot2], `dplyr` [@dplyr], `readr` [@readr], `tibble` [@tibble], `here` [@here], `kableExtra` [@kableExtra], `janitor` [@janitor], and `knitr` [@knitr].
 
@@
 
-data <- read.csv(here::here("inputs/data/cleaned_categorized_data.csv"))
+data <- read.csv(here::here("data/analysis_data/cleaned_categorized_data.csv"))
 # Delete the column
@@
 However, in response to the COVID-19 Pandemic, from 2020 to 2021, the GSS transitioned to web surveys as the primary method of collecting data.
-The GSS had a target population of English or Spanish speaking adults (18 years or older) living in households in the United States [@gssFAQ].
+The GSS had a target population of English or Spanish speaking adults (18 years or older) living in households in the United States [@GSS].
 The broad criteria allows a wide range of participants to partake in the survey.
 However, individuals who do not meet the target population are considered out of scope for the survey.
-Individuals who are not English or Spanish speaking, with mental and/or physical conditions that prevent them from participating in the survey are considered to be out of scope for the GSS [@gssFAQ].
+Individuals who are not English or Spanish speaking, with mental and/or physical conditions that prevent them from participating in the survey are considered to be out of scope for the GSS [@GSS].
 Adjustments in the GSS's respondent selection process, including changes to the Kish grid methodology, pose additional challenges by potentially skewing the demographic representation of respondents.
@@
 #| fig-cap: Categorical Working Hour Comparison between the Years
-#| fig-subcap: ["Asian Financial Crisis (1998)","World Financial Crisis(2008)","During Covid-19 Pandemic (2021)", "Total"]
+#| fig-subcap: ["Asian Financial Crisis (1998)","World Financial Crisis (2008)","During Covid-19 Pandemic (2021)", "Total"]
 #| layout-ncol: 2
@@
 
-data <- read.csv(here::here("inputs/data/cleaned_categorized_data.csv"))
+data <- read.csv(here::here("data/analysis_data/cleaned_categorized_data.csv"))
 data <- data[c(2:ncol(data))]
+data <- data[1:6,]
 # Get rid of the first letter X for each of the years
@@
 # Calculate percentages
-data <- read.csv(here::here("inputs/data/cleaned_categorized_data.csv"))
+data <- read.csv(here::here("data/analysis_data/cleaned_categorized_data.csv"))
 data <- data[c(2:ncol(data))]
@@
 
-data <- read.csv(here::here("inputs/data/cleaned_categorized_data.csv"))
+data <- read.csv(here::here("data/analysis_data/cleaned_categorized_data.csv"))
 data <- data[c(3:ncol(data))]
@@
 non_response_data <- data.frame(years,non_response_rate)
+non_response_data <-non_response_data[19:34,]
 
@@
 
-data <- read.csv(here::here("inputs/data/cleaned_data.csv"))
+data <- read.csv(here::here("data/analysis_data/cleaned_data.csv"))
 # Get rid of the first letter X for each of the years
@@
 
-average_hours <- data.frame(cbind(averages,years))
+average_hours <- data.frame(cbind(years,averages))
 
-ggplot(average_hours,aes(x=years,y=averages)) +
-  geom_bar(stat="identity") + 
-  theme_minimal() + # Make the theme neater
-  labs(x = "Year", y = "Average Working Hour") +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom")
+kable(average_hours,row.names = FALSE)|>
+  kable_styling()
 ```
@@
 
-## Nonreponse Rate
+## Nonresponse Rate
 
@@
 
-For future labour market survey research, we refer to the method proposed by Groves and Peytcheva [@Groves_Peytcheva_2008] above to eliminate non-response rates and bias as much as possible.
+For future labour market survey research, we refer to the method proposed by @Groves_Peytcheva_2008 above to eliminate non-response rates and bias as much as possible.
 We recommend a hybrid offline and online survey design; this approach can improve participation rates and data representativeness by accommodating a wider range of respondent preferences and accessibility.

### 2024-03-14 scripts/00-simulate_data.R

@@ -1,13 +1,24 @@
+#### Preamble ####
+# Purpose: Simulates number of reports in different amount of hours working
+# Author: Mingjia Chen, Catherine Punnoose, Tianen (Evan) Hao
+# Date: 14 March 2023 
+# Contact: mingjia.chen@mail.utoronto.ca 
+# License: MIT
+# Pre-requisites: none
+
+#### Workspace setup ####
 library(tibble)
 library(dplyr)
 library(tidyr)
 
+#### Simulate data ####
 # Define years and work hours categories
-years <- c(1972, 1973, 1974, 1975, 1976, 1977, 1978, 1980, 1981, 1982, 
-           1983, 1984, 1985, 1986, 1987, 1988, 1989, 1990, 1991, 1992, 
-           1993, 1994, 1995, 1996, 1997, 1998, 1999, 2000, 2001, 2002, 
-           2003, 2004, 2005, 2006, 2008, 2010, 2012, 2014, 2016, 2018, 
-           2021, 2022)
+
+# Some of the years are not included due to the fact that many years are
+# missing from the GSS data set
+years <- c(1992, 1993, 1994, 1995, 1996, 1997, 1998, 1999, 2000, 2001, 
+           2002, 2003, 2004, 2005, 2006, 2008, 2010, 2012, 2014, 2016, 
+           2018, 2021, 2022)
 work_hours_categories <- c("No Response", "0-20", "21-40", "41-60", "61-80")
 
 # Simulate data

### 2024-03-14 scripts/01-download_data.R

@@ -9,3 +9,5 @@
 
 # The download of the raw data requires filtering and browsing The General Social Survey (https://gss.norc.org/documents/stata/GSS_stata.zip). 
 # The whole replication package is available on-site for downloading regarding to the GSS Codebook.
+
+# Refer back to Readme for instructions downloading the data set for replication.

### 2024-03-14 scripts/03-data_tabling.R

@@ -1,5 +1,5 @@
 #### Preamble ####
-# Purpose: GSS Tables and Graphs for the Paper
+# Purpose: Code for replicating GSS Tables and Graphs in the Paper
 # Author: Mingjia Chen, Catherine Punnoose, Tianen (Evan) Hao
 # Date: 11 March 2024 
 # Contact: mingjia.chen@mail.utoronto.ca 

### 2024-03-14 paper/paper.qmd
Update writings
Update in-text citation formating

@@
 However, in response to the COVID-19 Pandemic, from 2020 to 2021, the GSS transitioned to web surveys as the primary method of collecting data.
+
 The GSS had a target population of English or Spanish speaking adults (18 years or older) living in households in the United States [@GSS].
@@
 Individuals who are not English or Spanish speaking, with mental and/or physical conditions that prevent them from participating in the survey are considered to be out of scope for the GSS [@GSS].
+
 Adjustments in the GSS's respondent selection process, including changes to the Kish grid methodology, pose additional challenges by potentially skewing the demographic representation of respondents.
@@
 By concentrating efforts on a more manageable subset of challenging cases for additional attempts, subsampling has the potential to minimize both response error and nonresponse bias [@gssCodebook2014].
+
 The GSS's approach to managing non-responses underwent changes, notably in its recent iterations – specifically during the COVID-19 Pandemic.
@@
 Historically, the survey employed subsampling techniques to mitigate the impact of non-responses, ensuring a representative dataset.
+
 However, with the introduction of web-based surveys, new categories like "Skipped on Web" were introduced to categorize non-responses.
-This change raises questions about the comparability of data across years and the potential for increased non-response rates (@fig-nonresponse-rate).
+This change raises questions about the comparability of data across years and the potential for increased non-response rates.
 Non-responses can significantly affect the analysis of labour market trends, particularly in capturing the full extent of unemployment or underemployment during economic downturns.
@@
 GSS Data [^1] provides hours worked before and after a severe recession to reveal the trend of fewer hours worked during periods of economic instability, as @fig-ave-hour-comparison shows.
-The research perspective of @Wang_Madsen_Steiner_2016 shows that during the 2008 financial crisis, working hours in industries such as manufacturing and construction decreased significantly, mainly due to their direct link to the economic cycle.
+@Wang_Madsen_Steiner_2016 shows that during the 2008 financial crisis, working hours in industries such as manufacturing and construction decreased significantly, mainly due to their direct link to the economic cycle.
 These industries tend to respond quickly to economic downturns because of their reliance on consumer demand and investment, which typically decline during financial crises.
@@
 By analyzing GSS data and @fig-ave-hour-comparison shows that 2021, a pandemic year, has experienced a more serious decline in working hours than in 1998 and 2008.
-The research of
 @Chen_Yeh_2021 explains that this is because sectors that have traditionally been limited to physical presence, such as retail and hospitality, have faced even more significant challenges during COVID compared with historical economic crises, which have led to more substantial job losses and reduced hours.
@@
 
-We agree that strong measures should be in place to ensure participant confidentiality and data protection, as mentioned in the GSS codebook [@gssCodebook].
+We agree that strong measures should be in place to ensure participant confidentiality and data protection, as mentioned in @gssCodebook.
 This involves using a secure database to store sensitive information and encrypting participant details to prevent unauthorized access.
@@
 Recognizing the risk of sampling bias, whereby certain groups may be over-represented, we have diversified our outreach methods.
-Inspired by the GSS codebook [@gssCodebook], we recommend that new survey approaches post-2020 could reach participants through a variety of channels, including social media, community communications, and local organizations to ensure a broad range of demographics.
+Inspired by @gssCodebook, we recommend that new survey approaches post-2020 could reach participants through a variety of channels, including social media, community communications, and local organizations to ensure a broad range of demographics.
 

### 2024-03-15 scripts/04-test_data.R
update scripts for testing data

@@ -12,7 +12,7 @@
 library(dplyr)
 
 #### Test data ####
-data <- read.csv(here::here("inputs/data/cleaned_categorized_data.csv"))
+data <- read.csv(here::here("data/analysis_data/cleaned_categorized_data.csv"))
 test_non_negative <- all(select(data, -work_hours) >= 0)
 print(test_non_negative)
 #The result shows that the year columns does not contain non-negative values.
@@ -44,3 +44,26 @@ test_data_types <- all(sapply(data[,-c(1,2)], is.integer))
 print(test_data_types)
 #The data is consistent as everything except working hours are integers.
 
+
+# 6. Check that responses range from 1974 through 2022 #
+min(colnames(data)[2:36]) <= 1972
+max(colnames(data)[2:36]) >= 2022
+
+# 7. Check number of work hours categories
+data$work_hours |>
+  unique() |>
+  length() == 7
+
+#8. Check number of columns(work_hours + years)
+colnames(data) |>
+  unique() |>
+  length() == 37
+
+#9. Check if the totals are consistent
+sum(data[1:6,3]) == data[7,3]
+
+total <- 0
+for(i in 3:36){
+  total <- total + data[3,i] 
+}
+total == data[3,37]

### 2024-03-17 scripts/02-data_cleaning.R
update path

@@ -16,7 +16,7 @@ library(here)
 
 #### Clean data ####
 # load dataset that has been cropped for analysis
-data <- read.csv(here::here("inputs/data/cropped_data.csv"))
+data <- read.csv(here::here("data/raw_data/cropped_data.csv"))
 
 # the first column of the dataset is the names of the rows
 # so we renamed the row names based on first column and 
@@ -38,7 +38,7 @@ colnames(data) <- gsub("X", "", colnames(data))
 rownames(data)[1:4] <- c("Inapplicable","No answer","Do not Know/Cannot Choose","Skipped on Web")
 
 # Save the cleaned data
-write.csv(data, "inputs/data/cleaned_data.csv")
+write.csv(data, "data/analysis_data/cleaned_data.csv")
 
 #### Categorize Data #####
 colnames(data)[1] <- "work_hours"
@@ -114,4 +114,4 @@ cate_data <- rbind(No_Response,tweenties,forties,sixties,eighties,more,total)
 cate_data <- data.frame(cbind(Hours,cate_data))
 colnames(cate_data) <- year
 
-write.csv(cate_data,"inputs/data/cleaned_categorized_data.csv")
+write.csv(cate_data,"data/analysis_data/cleaned_categorized_data.csv")

### 2024-03-17 scripts/02-data_cleaning.R
Fix Data errors

@@ -18,16 +18,7 @@ library(here)
 # load dataset that has been cropped for analysis
 data <- read.csv(here::here("data/raw_data/cropped_data.csv"))
 
-# the first column of the dataset is the names of the rows
-# so we renamed the row names based on first column and 
-#deleted the column at the end
-row_number <- nrow(data)
-for (i in 1:row_number) {
-  rownames(data)[i] = data[i,1]
-}
-
-# Delete the column
-data <- data[c(2:ncol(data))]
+colnames(data)[1] <- "work_hours"
 
 # Get rid of the first letter X for each of the years
 colnames(data) <- gsub("X", "", colnames(data))
@@ -35,71 +26,63 @@ colnames(data) <- gsub("X", "", colnames(data))
 # Rename part of the row names 
 #(i.e. change .i Inapplicable into Inapplicable for better
 #data representation) 
-rownames(data)[1:4] <- c("Inapplicable","No answer","Do not Know/Cannot Choose","Skipped on Web")
+data[1:4,1] <- c("Inapplicable","No answer","Do not Know/Cannot Choose","Skipped on Web")
 
 # Save the cleaned data
 write.csv(data, "data/analysis_data/cleaned_data.csv")
 
 #### Categorize Data #####
-colnames(data)[1] <- "work_hours"
-colnames(data) <- gsub("X", "", colnames(data))
 cate_data <- data
 
 year <- colnames(data)
 Hours <- c("No Response","0-20","21-40","41-60","61-80","80+","Total")
 
-col_number <- ncol(cate_data) -1
+col_number <- ncol(cate_data)-1
 
 #summarize all the responses in one category
-filtered_df1 <- cate_data %>%
-  filter(work_hours < 20) 
+#0-20
+filtered_df1 <- cate_data[5:25,]
 
-tweenties <- rep(0, 35)
+tweenties <- rep(0, 36)
 for(i in 1:col_number){
   tweenties[i] <- sum(filtered_df1 [, i+1])
 }
 
-filtered_df2 <- cate_data %>%
-  filter(work_hours < 40) %>%
-  filter(work_hours > 20)
+#21-40
+filtered_df2 <- cate_data[26:45,]
 
-forties <- rep(0, 35)
+forties <- rep(0, 36)
[…]

### 2024-03-17 paper/paper.qmd
draw a little graph for now

@@
 # Get rid of the first letter X for each of the years
-colnames(data)[1] <- "work_hours"
 colnames(data) <- gsub("X", "", colnames(data))
@@
 
-\break
+```{r}
+#| label: fig-hour-working-percentage
+#| fig-cap: Average Working Hours Percentages 
+#| echo: false
+#| warning: false
+#| message: false
+#| 
+data <- read.csv(here::here("data/analysis_data/cleaned_categorized_data.csv"))
+data <- data[c(2:ncol(data))]
+# Get rid of the first letter X for each of the years
+colnames(data) <- gsub("X", "", colnames(data))
+work_hours <- rep(data$work_hours,35)
+years <- colnames(data)[2:36]
+years <- rep(years,each=7)
+
+responses <- unname(unlist(data[c(2:36)]))
+
+data_long <- data.frame(cbind(work_hours,years,responses))
+Totals <- filter(data_long, work_hours == "Total")
+Subtotals <- filter(data_long, work_hours == "No Response")
+Totals$responses <- as.numeric(Totals$responses)
+Subtotals$responses <- as.numeric(Subtotals$responses)
+Subtotals <- mutate(Subtotals, subtotal = Totals$responses - Subtotals$responses)
+
+data_perc <- data_long %>%  filter(years>=1993) %>% 
+  filter(work_hours != "Total") %>%
+  filter(work_hours != "No Response")
+
+# Generate heatmap
+generate_heatmap <- function(
+    ggplot_data,
+    xlabel = NULL,
+    ylabel = NULL,
+    position = NULL,
+    angle = 45,
+    hjust = 1,
+    vjust = 1
+) {
+
+  ggplot_data +
+    geom_tile() +
+    scale_fill_gradient2(low = "white", high = "darkblue", guide = "colorbar") +
+    theme(
+      axis.text.x = element_text(angle = angle, vjust = vjust, hjust = hjust)
+    ) +
+    theme(legend.position = position) +
+    labs(
+      x = xlabel,
+      y = ylabel,
+    )
+}
+
+ggplot_data <- inner_join(data_perc, Subtotals, 
+                          by = c("years"))
+ggplot_data$responses.x <- as.numeric(ggplot_data$responses.x)
+ggplot_data <- mutate(ggplot_data,Percentage = responses.x/subtotal)
+
+generate_heatmap(
+  ggplot_data |>
+    ggplot(aes(x = years, y = work_hours.x, fill = Percentage)),
+  xlabel = "Year of Data Collected",
+  ylabel = "Number of Hours Worked Last Week"
+)
+
+```
 

### 2024-03-18 paper/paper.qmd
Update new dataset

@@
   - Tianen (Evan) Hao
-thanks: "Code and data are available at: https://github.com/ShadyEvan4830/Labour_Market_Resilience.git"
+thanks: "Code and data are available at: https://github.com/ShadyEvan4830/Labour_Market_Resilience.git. Thank Professor Alexander so much for the fantastic feedback."
 date: March 11, 2024
@@
 
-Initial findings show disparities: younger workers, those with less education, and women face significant work-hour reductions during crises.
-This underscores the need for targeted policy interventions to address these disparities and strengthen labour market resilience.
+Initial findings show disparities: workers faced significant reductions in working hours during the crisis, with studies by [@Chen_Yeh_2021] and [@Singh_Shirazi_Turetken_2022] showing that women face a more severe job impact due to their unique social obligations.
+This highlights the need for targeted policy interventions to address these differences and enhance labour market resilience.
 
@@
 #| label: fig-cate-comparisons
-#| fig-cap: Categorical Working Hour Comparison between the Years
+#| fig-cap: Categorical Working Hours of last Week Comparison between the Years with Critial Financial Crisis
 #| fig-subcap: ["Asian Financial Crisis (1998)","World Financial Crisis (2008)","During Covid-19 Pandemic (2021)", "Total"]
@@
   theme_minimal() + # Make the theme neater
-  labs(x = "Hours of Working", y = "Number of Reports") +
+  labs(x = "Hours of Working Last Week", y = "Number of Responses") +
   scale_color_brewer(palette = "Set1") +
@@
 
-## Average Working Hour Comparison Between Financial Events
+## Average Working Hour Comparison Between Financial Crisis
 
@@
 #| label: fig-ave-hour-comparison
-#| fig-cap: Average Working Hours Comparison between Financial Events
+#| fig-cap: Average Working Hours Comparison between Financial Crisis
 #| echo: false
@@
 
+## Nonresponse Rate
+
+As we illustrated in @fig-nonresponse-rate, non-response rates may also help indicate significant differences in participants and data collection over the years.
+For example, although we can still see a slight increase from 1992 to 2022 (no data for 1992), this suggests that a gradual rise in non-response rates from 1992 to 2022 may signal a decline in participant engagement and accessibility Variety.
+We speculate that this trend may be attributed to the rise of digital communications, privacy concerns, and survey fatigue.
+Demographic changes and technological advances, such as the widespread use of mobile devices, also play a role.
+Therefore, adapting survey methods to these changes is critical to maintaining data quality and representativeness.
+
 ```{r}
@@
 #| message: false
-#| 
+
 data <- read.csv(here::here("data/analysis_data/cleaned_categorized_data.csv"))
@@
   filter(work_hours != "No Response")
+
+# Reference Helper Function code from 
+# https://github.com/christina-wei/Financial-Wellness-in-US/blob/main/scripts/04-helper_functions.R
 
@@
 
-## Nonresponse Rate
+```{r}
+#| label: fig-demographic-comparison
+#| fig-cap: Working Hours Comparisons with Demographic factors
+#| layout-ncol: 2
+#| echo: false
+#| warning: false
+#| message: false
 
-Non-response rates we illustrated in @fig-nonresponse-rate, in addition, could help indicate a significant difference in participants and data collection between the years.
-The year 1972, for example, is evidence of the gap in the data set; even though it is included in the data set, the non-response rate is 100%, meaning that no answers to this question were collected during that year.
-The non-response rate in general is similar among the years, not indicating significant differences between the years even during the financial crisis.
+sup_data <- read.csv(here::here("data/analysis_data/supplementary_data.csv"))
+
+```
 

### 2024-03-18 scripts/02-data_cleaning.R

@@ -13,6 +13,7 @@ library(knitr)
 library(dplyr)
 library(kableExtra)
 library(here)
+library(haven)
 
 #### Clean data ####
 # load dataset that has been cropped for analysis
@@ -100,3 +101,49 @@ colnames(cate_data) <- year
 
 
 write.csv(cate_data,"data/analysis_data/cleaned_categorized_data.csv")
+
+##### Additional Data Set for Result Section ######
+#Code Referenced from GSS website
+#https://gssdataexplorer.norc.org/MyGSS
+library(foreign)
+read.dct <- function(dct, labels.included = "yes") {
+  temp <- readLines(dct)
+  temp <- temp[grepl("_column", temp)]
+  switch(labels.included,
+         yes = {
+           pattern <- "_column\\(([0-9]+)\\)\\s+([a-z0-9]+)\\s+(.*)\\s+%([0-9]+)[a-z]\\s+(.*)"
+           classes <- c("numeric", "character", "character", "numeric", "character")
+           N <- 5
+           NAMES <- c("StartPos", "Str", "ColName", "ColWidth", "ColLabel")
+         },
+         no = {
+           pattern <- "_column\\(([0-9]+)\\)\\s+([a-z0-9]+)\\s+(.*)\\s+%([0-9]+).*"
+           classes <- c("numeric", "character", "character", "numeric")
+           N <- 4
+           NAMES <- c("StartPos", "Str", "ColName", "ColWidth")
+         })
+  temp_metadata <- setNames(lapply(1:N, function(x) {
+    out <- gsub(pattern, paste("\\", x, sep = ""), temp)
+    out <- gsub("^\\s+|\\s+$", "", out)
+    out <- gsub('\"', "", out, fixed = TRUE)
+    class(out) <- classes[x] ; out }), NAMES)
+  temp_metadata[["ColName"]] <- make.names(gsub("\\s", "", temp_metadata[["ColName"]]))
+  temp_metadata
+}
+
+read.dat <- function(dat, metadata_var, labels.included = "yes") {
+  read.table(dat, col.names = metadata_var[["ColName"]])
+}
+
+
+GSS_metadata <- read.dct(here::here("data/raw_data/GSS.dct"))
+GSS_ascii <- read.dat(here::here("data/raw_data/GSS.dat"), GSS_metadata)
+attr(GSS_ascii, "col.label") <- GSS_metadata[["ColLabel"]]
+additional_data <- GSS_ascii
+
[…]

### 2024-03-18 paper/paper.qmd
Update paper

@@
 This paper uses U.S.
-General Social Survey (GSS) [@GSS] data to examine the "number of hours worked last week" as a key measure of labour engagement.
+General Social Survey (GSS) data to examine the "number of hours worked last week" as a key measure of labour engagement.
 We hypothesize that economic downturns lead to decreased labour engagement, seen in reduced work hours, impacting labour groups differently.
@@
 
-Initial findings show disparities: workers faced significant reductions in working hours during the crisis, with studies by [@Chen_Yeh_2021] and [@Singh_Shirazi_Turetken_2022] showing that women face a more severe job impact due to their unique social obligations.
+Initial findings show disparities: workers faced significant reductions in working hours during the crisis.
+In 2021, more than 50% of workers worked 21-40 hours, and only more than 10% will work 41-60 hours; while in 2018, an average economic year, more than 40% of workers will work 41-60 hours.
+Furthermore, studies by @Chen_Yeh_2021 and @Singh_Shirazi_Turetken_2022 show that women face a more severe job impact due to their unique social obligations.
 This highlights the need for targeted policy interventions to address these differences and enhance labour market resilience.
@@
 The paper uses data collected from the US General Social Survey (GSS) from NORIC at the University of Chicago [@GSS].
-From the dataset, this paper focuses on the "number of hours worked last week" variable, from the years 1972 to 2022.
+From the dataset, this paper focuses on the "number of hours worked last week" variable, from the years 1992 to 2022.
 This longitudinal approach allows us to compare labour dynamics across different economic downturns, including the 1998 Asian Financial Crisis, the 2008 Global Financial Crisis, and the COVID-19 pandemic in 2020.
@@
 
-From 1972 to 2018, the GSS was conducted through face-to-face interviews.
+From 1992 to 2018, the GSS was conducted through face-to-face interviews.
 In-person interviews facilitated a richer data collection environment, where interviewers could clarify ambiguities and probe deeper into responses.
@@
 The survey's methodology has several strengths.
-From 1972 to 2018, data was gathered through face-to-face interviews, enabling interviewers to capture diverse and comprehensive information, providing a deeper understanding of respondents.
+From 1992 to 2018, data was gathered through face-to-face interviews, enabling interviewers to capture diverse and comprehensive information, providing a deeper understanding of respondents.
 Another notable strength is the survey's consistency.
-The General Social Survey (GSS) has maintained a uniform approach since 1972, with minimal alterations in questions and data collection methods each year.
+The General Social Survey (GSS) has maintained a uniform approach since 1992, with minimal alterations in questions and data collection methods each year.
 This consistency facilitates clear year-to-year analyses for researchers.
@@
 
-Since 1972, the General Social Survey (GSS) has been gathering data primarily through face-to-face interviews, during which participants were interviewed using a structured questionnaire.
+Since 1992, the General Social Survey (GSS) has been gathering data primarily through face-to-face interviews, during which participants were interviewed using a structured questionnaire.
 This approach persisted until the onset of the COVID-19 Global Pandemic, which resulted in the suspension of data collection for the year 2020.
@@
 This change raises questions about the comparability of data across years and the potential for increased non-response rates.
-Non-responses can significantly affect the analysis of labour market trends, particularly in capturing the full extent of unemployment or underemployment during economic downturns.
+Non-responses (@fig-nonresponse-rate) can significantly affect the analysis of labour market trends, particularly in capturing the full extent of unemployment or underemployment during economic downturns.
 The handling of these non-responses requires scrutiny to assess how it might influence findings on work hours and job stability across different demographic groups and economic sectors.
@@
 ```
+\break
+
+The data depicted in @fig-hour-working-percentage illustrates the average yearly working hours.
+Initially, it is evident that the highest average yearly working hours fall within the range of 21-40 hours.
+Particularly notable are the years 2021 and 2022, which exhibit the highest percentage of average working hours.
+One potential explanation for this pattern could be linked to the post-pandemic economy, marked by efforts towards economic recovery and escalating costs across various industries.
+As more individuals reentered the workforce, it is plausible that this contributed to the elevated average working hours observed in 2021 and 2022.
+
+@fig-hour-working-percentage indicates that the second most common range of average working hours is between 41-60 hours, suggesting that a significant portion of the population works within this time frame.
+Following this, the analysis highlights that the third most common range is 0-20 hours, indicating a substantial number of individuals who work part-time or have limited working hours.
+As the analysis progresses, it notes that the averages of 61-80 hours and 80+ hours represent progressively smaller percentages of average working hours.
+This implies that fewer individuals work such long hours compared to those in the previous ranges.
+Finally, it specifies that the category of 80+ hours represents the smallest percentage, indicating that only a minority of individuals work exceptionally long hours.
+Overall, this analysis provides insight into the distribution of working hours, highlighting common patterns and indicating trends towards fewer individuals working extremely long hours.
 
@@
 #| fig-cap: Working Hours Comparisons with Demographic factors
+#| fig-subcap: ["Average Age by Each Year","Percentage of Female Respondent by Each Year"]
 #| layout-ncol: 2
@@
 
+average_age_by_year <- aggregate(AGE ~ YEAR, data = sup_data, FUN = mean)
+sex_counts_by_year <- aggregate(SEX ~ YEAR, data = sup_data, function(x) mean(x == 2) * 100) #calculate percentage of females each year
+
+average_age_by_year <- average_age_by_year |> 
+  filter(YEAR%in%c(1998,2008, 2010,2018,2021))
+
+sex_counts_by_year <- sex_counts_by_year |> 
+  filter(YEAR%in%c(1998,2008,2010,2018,2021))
+
+average_ages <- average_age_by_year$AGE
+average_gender <- sex_counts_by_year$SEX
+
+data <- read.csv(here::here("data/analysis_data/cleaned_data.csv"))
+# Get rid of the first letter X for each of the years
+colnames(data) <- gsub("X", "", colnames(data))
+
+#Histogram of average working hours for 2008, 2021, 2022, and Total
+hist_data <- select(data, work_hours,"1998","2008","2010","2018","2021")
+hist_data <- hist_data[5:94,]
+
+num <- 5 #number of years
+sum <- rep(0,num)
+total_people <- rep(0,num)
+for(i in 1:num){
+  total_people[i] <- sum(hist_data[, i+1])
+}
+hist_data[, 1] <- sapply(hist_data[, 1], as.numeric)
+hist_data[90,1] <- 90
+
+sum[1] <- sum(hist_data$"1998" * hist_data$work_hours)
+sum[2] <- sum(hist_data$"2008" * hist_data$work_hours)
+sum[3] <- sum(hist_data$"2010" * hist_data$work_hours)
+sum[4] <- sum(hist_data$"2018" * hist_data$work_hours)
+sum[5] <- sum(hist_data$"2021" * hist_data$work_hours)
+
+averages <- round(sum/total_people) 
+years <- c("1998","2008","2010","2018","2021")
+
+average_hours <- data.frame(cbind(years,averages))
+
+gg_data <- cbind(average_hours,average_ages,average_gender)
+
+ggplot(gg_data,aes(x=years,y=average_ages)) +
+  geom_bar(stat="identity") + 
+  theme_minimal() + # Make the theme neater
+  labs(x = "Years", y = "Average Age") +
+  scale_color_brewer(palette = "Set1") +
+  theme(legend.position = "bottom")
+
+ggplot(gg_data,aes(x=years,y=average_gender)) +
+  geom_bar(stat="identity") + 
+  theme_minimal() + # Make the theme neater
+  labs(x = "Years", y = "Percentage of Females (%)") +
+  scale_color_brewer(palette = "Set1") +
+  theme(legend.position = "bottom")
 ```
+
+@fig-demographic-comparison presents a comparison of average ages across different years, specifically for 1998, 2008, 2010, 2018, and 2021.
+The y-axis represents the average age, and the x-axis denotes the years.
+The bars show a slight decrease in the average age in 2021 compared to the previous years, suggesting a younger demographic in the most recent year displayed.
+It also illustrates the percentage of females within the data for the same years as shown in @fig-demographic-comparison.
+The y-axis indicates the percentage of females, while the x-axis represents the years.
+The bars are relatively even, demonstrating a consistent representation of females across the selected years, with a very slight variation.
+
+Both figures are titled "Working Hours Comparisons with Demographic factors," implying that the data presented may be used to analyze the relationship between demographic characteristics (age and gender) and working hours, although the specific hours worked are not shown in these charts.
+The consistent layout and design of the charts facilitate a clear and direct comparison of demographic trends over the years.
 
@@
 
-We agree that strong measures should be in place to ensure participant confidentiality and data protection, as mentioned in @gssCodebook.
+We agree that strong measures should be in place to ensure participant confidentiality and data protection, as mentioned in the @gssCodebook.
 This involves using a secure database to store sensitive information and encrypting participant details to prevent unauthorized access.
@@
 Recognizing the risk of sampling bias, whereby certain groups may be over-represented, we have diversified our outreach methods.
-Inspired by @gssCodebook, we recommend that new survey approaches post-2020 could reach participants through a variety of channels, including social media, community communications, and local organizations to ensure a broad range of demographics.
+Inspired by the @gssCodebook, we recommend that new survey approaches post-2020 could reach participants through a variety of channels, including social media, community communications, and local organizations to ensure a broad range of demographics.
 
@@
 Our analysis grounded in the rich dataset provided by the General Social Survey (GSS) [^1], navigates through a complex terrain of labour market dynamics in the wake of economic crises.
-However, as mentioned in the data @sec-data, several limitations inherent to the dataset and the broader research approach necessitate a cautious interpretation of our findings.
+However, as mentioned in the @sec-data section, several limitations inherent to the dataset and the broader research approach necessitate a cautious interpretation of our findings.
 
-The original data only provides simple data on working hours, but in @gssCodebook, GSS has a detailed explanation of the data survey method, such as interviewing random people through questionnaires.
+The original data only provides simple data on working hours, but in [@gssCodebook], GSS has a detailed explanation of the data survey method, such as interviewing random people through questionnaires.
 The sensitive nature of questions related to economic hardships and employment challenges may lead to a degree of response bias.
@@
 
-Finally, our paper also has certain limitations in processing data as shown in data @sec-data.
+Finally, our paper also has certain limitations in processing data as shown in @sec-data section.
 One limitation stems from our decision to analyze the years immediately following the economic crisis (2010 and 2021) rather than the year immediately following the recession itself.
@@
 In addressing non-response rates within labour market surveys, @Groves_Peytcheva_2008 provides some suggestions for directions for our consideration.
-They advocate for tailored communication and mixed-mode survey approaches as effective measures against non-response bias (Journal of Official Statistics, 24(2), 167-189).
+They advocate for tailored communication and mixed-mode survey approaches as effective measures against non-response bias [@Groves_Peytcheva_2008].
 For instance, future research could look into the success of the Health and Retirement Study, which employs a mixed-mode design, combining in-person interviews with telephone and online follow-ups to accommodate participant preferences and improve response rates.
@@
 To tackle response bias, a common hurdle in surveys on sensitive topics like economic impact, future efforts could lean more heavily into techniques that safeguard participant anonymity and confidentiality.
-For example, the Pew Research Center's [@Pew_Research_Center_2021] method of ensuring anonymity in their political opinion polls could serve as a model, enhancing respondent confidence and honesty.
+For example, the @Pew_Research_Center_2021's research method of ensuring anonymity in their political opinion polls could serve as a model, enhancing respondent confidence and honesty.
 Briefly, their approach is characterized by random sampling to select representativeness.
@@
 
-For future labour market survey research, we refer to the method proposed by @Groves_Peytcheva_2008 above to eliminate non-response rates and bias as much as possible.
+For future labour market survey research, we refer to the method proposed by Groves and Peytcheva (2008) above to eliminate non-response rates and bias as much as possible.
 We recommend a hybrid offline and online survey design; this approach can improve participation rates and data representativeness by accommodating a wider range of respondent preferences and accessibility.

### 2024-03-18 paper/paper.qmd
Update paper

@@
 The purpose of this variable is to collect the year the survey was conducted.
+To collect demographic data, specifically age and gender, the datasets “age” and “sex” were used.
+The two datasets are used to further analyze age groups and genders to working hours.
 
@@
 | year     | year       | The year of the survey recorded | 2007    |
+| AGE      | AGE        | The age of the respondents      | 23      |
+| SEX      | SEX        | The gender of the respondents   | MALE    |
 
@@
 
+## Percentage of Working Hours Responses
 ```{r}
@@
 
+## Demographic Factors
+
 ```{r}
@@
 @fig-demographic-comparison presents a comparison of average ages across different years, specifically for 1998, 2008, 2010, 2018, and 2021.
-The y-axis represents the average age, and the x-axis denotes the years.
 The bars show a slight decrease in the average age in 2021 compared to the previous years, suggesting a younger demographic in the most recent year displayed.
-It also illustrates the percentage of females within the data for the same years as shown in @fig-demographic-comparison.
-The y-axis indicates the percentage of females, while the x-axis represents the years.
+It illustrates the percentage of females within the data for the same years as shown in @fig-demographic-comparison as well.
 The bars are relatively even, demonstrating a consistent representation of females across the selected years, with a very slight variation.
 
-Both figures are titled "Working Hours Comparisons with Demographic factors," implying that the data presented may be used to analyze the relationship between demographic characteristics (age and gender) and working hours, although the specific hours worked are not shown in these charts.
-The consistent layout and design of the charts facilitate a clear and direct comparison of demographic trends over the years.
+Both @fig-demographic-comparison-1 and @fig-demographic-comparison-2 analyze the relationship between demographic characteristics (age and gender) and working hours.
+The demographic factors do not vary dramatically, indicating that age and gender may not play a significant role in terms of work hours in a week.
 
@@
 Our analysis grounded in the rich dataset provided by the General Social Survey (GSS) [^1], navigates through a complex terrain of labour market dynamics in the wake of economic crises.
-However, as mentioned in the @sec-data section, several limitations inherent to the dataset and the broader research approach necessitate a cautious interpretation of our findings.
+However, as mentioned in the [Data] section, several limitations inherent to the dataset and the broader research approach necessitate a cautious interpretation of our findings.
 
@@
 
-Finally, our paper also has certain limitations in processing data as shown in @sec-data section.
+Finally, our paper also has certain limitations in processing data as shown in [Data] section.
 One limitation stems from our decision to analyze the years immediately following the economic crisis (2010 and 2021) rather than the year immediately following the recession itself.
